---
title: "Soc-Xsit Analysis and Vizualizations"
author: "Kyle MacDonald"
date: "January 17, 2015"
output: html_document
---

Clear workspace and set working directory 

```{r clear workspace, echo=F, warning=F}
rm(list=ls())
source("useful.R")
library(pander)
library(magrittr)
library(gridExtra)
library(tidyr)
library(directlabels)
```

Read in data from all 3 Experiments:

* Large scale experiment manipulating attention and memory demands
* Replication of Experiment 1 with more ecologically valid stimulus set
* Parametric manipulation of cue reliablity

```{r read data, echo=F, warning=F}
df_expt1 <- read.csv("../../data/soc_xsit_expt1_master_clean.csv")
df_expt2 <- read.csv("../../data/soc_xsit_live_expt2.csv")
df_expt3 <- read.csv("../../data/soc_xsit_reliabiliy_parametric_replication.csv",
                     stringsAsFactors = F)
df_expt3_original <- read.csv("../../data/soc_xsit_reliability_expt3.csv",
                     stringsAsFactors = F)
```

```{r, echo = F}
df_expt3 %<>% mutate(experiment = "replication",
                     rel_subj = to.n(rel_subj))

df_expt3 <- df_expt3_original %>% 
    mutate(experiment = "original") %>% 
    bind_rows(df_expt3)
```

## Experiment 1

### Get the number of subjects in each condition.  

```{r describe data, tidy=TRUE}
nsubs <- df_expt1 %>%
    group_by(condition, intervalNum, numPicN) %>%
    summarise(n_subs = n_distinct(subids))

pandoc.table(nsubs, style="rmarkdown")
```

### Do some minor data cleaning and create variables

Flag trials on which subs chose the target of eye gaze.

```{r expt1 target of gaze}
df_expt1 %<>% 
    mutate(trial_category = ifelse(dataset == "dy", "test",
                                   ifelse(exposureTrial == 1, "exposure", 
                                          ifelse(exampleTrial == 1, "example",
                                                 ifelse(testTrial == 1, "test",
                                                        NA))))) %>% 
    filter(trial_category != "example")

df_expo_expt1 <- df_expt1 %>%
    filter(trial_category == "exposure") %>%
    mutate(correct_exposure = ifelse(numPic == 6, 
                                     chosenIdx == faceIdx6,
                                     chosenIdx == faceIdx)) %>%
    select(subids, itemNum, correct_exposure, rt) %>% 
    rename(rt_exposure = rt) %>%
    filter(rt_exposure > 0) %>% 
    mutate(include_good_rt_exposure = ifelse(log(rt_exposure) > mean(log(rt_exposure)) + 
                                                 2 * sd(log(rt_exposure)) |
                                                 log(rt_exposure) < mean(log(rt_exposure)) - 
                                                 2 * sd(log(rt_exposure)),
                                             "exclude", "include"))

# Merge with exposure trial information. 
df_expt1 %<>% left_join(y = df_expo_expt1, by = c("subids", "itemNum"))
```

Flag subs in the social condition who performed worse than chance on exposure trials.

```{r expt 1 flag subs < 25% correct on exposure}
df_test_expo_correct <- df_expt1 %>%
    filter(condition == "Social", trial_category == "test") %>%
    group_by(subids, numPic) %>%
    summarise(mean_acc_exp = mean(correct_exposure)) %>%
    mutate(include_expo = ifelse(numPic == 2 & mean_acc_exp > 0.5, "include", 
                                 ifelse(numPic == 4 & mean_acc_exp > 0.25, "include",
                                        ifelse(numPic == 6 & mean_acc_exp > 0.17, "include", 
                                               ifelse(numPic == 8 & mean_acc_exp > 0.125, 
                                                      "include", "exclude"))))) %>% 
    select(subids, mean_acc_exp, include_expo) 

df_expt1 %<>% left_join(y = df_test_expo_correct, by = c("subids"))
```

Flag test trials with really slow or fast RTs (+/- 2SD).

```{r expt1 rt cleaning}
df_test_rt <- df_expt1 %>% 
    filter(trial_category == "test") %>% 
    rename(rt_test = rt) %>% 
    filter(rt_test > 0) %>% 
    mutate(include_good_rt_test = ifelse(log(rt_test) > mean(log(rt_test)) + 
                                             2 * sd(log(rt_test)) |
                                             log(rt_test) < mean(log(rt_test)) - 
                                             2 * sd(log(rt_test)),
                                         "exclude", "include")) %>% 
    select(subids, itemNum, include_good_rt_test)

df_expt1 %<>% left_join(y = df_test_rt, by = c("subids", "itemNum"))
```

Save filtered dataset for final analyses in manuscript.

```{r expt1 save clean dataset}
write.csv(x = df_expt1, 
          "../../paper/manuscript/soc-xsit-expt1-finalData.csv",
          row.names = F)
```

### Set up filters 

Get test trials for analysis. Here we have 2 filters:

* Remove fast/slow RTs
* Remove fast/slow RTs & subjects who performed below 
chance selecting gaze target on exposure trials

```{r expt1 test trials}
# just RT filter
df_test_expt1 <- df_expt1 %>%  
    filter(trial_category == "test", include_good_rt_test == "include",
           correct_exposure == T | condition == "No-Social")

# subject and trial level filter
df_test_expt1_filt <- df_expt1 %>% 
    filter(trial_category == "test") %>% 
    filter(include_good_rt_test == "include", 
           include_expo == "include" | condition == "No-Social") %>%
    filter(correct_exposure == T | condition == "No-Social")

df_expo_expt1_analysis <- df_expt1 %>%
    filter(trial_category == "exposure") %>% 
    filter(include_good_rt_exposure == "include", 
           include_expo == "include" | condition == "No-Social") %>%
    filter(correct_exposure == T | condition == "No-Social")
```

Get the number of subjects filtered out

```{r expt1 nsubs filtered}
df_n <- df_test_expt1 %>%
    group_by(condition) %>%
    summarise(n_subs = n_distinct(subids))

df_n_filt <- df_test_expt1_filt %>%
    group_by(condition) %>%
    summarise(n_subs_filt = n_distinct(subids)) %>%
    select(n_subs_filt)

df_n <- cbind(df_n, df_n_filt)

df_n
```

### Accuracy on exposure trials in social condition

Get means and CIs for each combination of number of referents and interval

```{r expt1 accuracy on exposure trials}
ms_expo_expt1 <-  df_test_expt1 %>%
    filter(condition == "Social") %>%
    group_by(numPic, intervalNum) %>%
    summarise(accuracy_exposure = mean(correct_exposure),
              ci_low = ci.low(correct_exposure),
              ci_high = ci.high(correct_exposure))
```

Now plot those means.

```{r expt 1 accuracy on exposure trials plot, echo=F}
ggplot(data=ms_expo_expt1, 
       aes(x=intervalNum, y=accuracy_exposure)) + 
    geom_pointrange(aes(ymin=accuracy_exposure - ci_low, 
                        ymax=accuracy_exposure + ci_high), 
                    width = .05, size=0.6) +
    geom_hline(aes(yintercept=1/numPic), linetype = "dashed") +
    scale_x_continuous(limits=c(-.9,8), breaks=c(0, 1, 3, 7)) +
    scale_y_continuous(limits=c(0,1)) +
    scale_colour_manual(values=c("#1f78b4", "red")) +
    facet_grid( ~ numPic, labeller = mf_labeller) + 
    xlab("Intervening Trials") + 
    ylab("Prop. Choosing Repeated Referent") +
    labs(colour = "Condition") +
    labs(linetype = "Trial Type") +
    guides(linetype=FALSE) +
    theme(text = element_text(size=14), 
          axis.title.y=element_text(vjust=1),
          axis.title.x=element_text(vjust=-0.3),
          legend.justification=c(0,0),
          legend.position = c(0,0)) 
```

### RT on exposure trials 

Next we compare reaction times across social/no-social at different 
levels of attention and memory demands.

```{r expt1 rt on exposure trials}
ms_expo_rt_expt1 <-  df_expo_expt1_analysis %>%
    group_by(numPic, intervalNum, condition) %>%
    summarise(mean_rt = mean(rt),
              ci_low = ci.low(rt),
              ci_high = ci.high(rt))
```

Now we plot mean reaction times for each condition.

```{r expt1 rt on exposure trials, echo=F}
# change factor labels 
ms_expo_rt_expt1$condition <- revalue(ms_expo_rt_expt1$condition,
                                      c("No-Social" = "No-Gaze","Social" = "Gaze"))
```

```{r expt1 plot rt on exposure trials, echo=F}
exp1_rt_exposure_plot <- ggplot(data=ms_expo_rt_expt1, 
                                aes(x=intervalNum, y=mean_rt, color = condition)) + 
    geom_linerange(aes(ymin=mean_rt - ci_low, 
                        ymax=mean_rt + ci_high), width = .05, size=1) +
    geom_point(size=5) +
    scale_x_continuous(limits=c(-.9,9.5), breaks=c(0, 1, 3, 7)) +
    geom_smooth(method="lm", se =F) +
    scale_y_continuous(limits=c(0,5200)) +
   # scale_colour_grey(start = 0.3, end = 0.6) +
    scale_colour_manual(values=c("#2c7fb8", "#e34a33")) +
    facet_grid( ~ numPic, labeller = mf_labeller) + 
    xlab("Interval Between Exposure and Test") + 
    ylab("Reponse Time (ms)") +
    labs(colour = "Condition") +
    labs(linetype = "Trial Type") +
    guides(linetype=FALSE, color=F) +
     theme(axis.title.x = element_text(colour="black",size=22,
                                      angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.text.x = element_text(colour="grey20",size=18,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.text.y = element_text(colour="grey20",size=18,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.title.y = element_text(colour="black",size=22,face="plain"),
          legend.position=c(0.1,0.2),
          legend.text = element_text(size=18),
          legend.title = element_text(size=20, face="bold"),
          strip.text = element_text(size=16),
          panel.grid.minor = element_blank(),
          panel.grid.major = element_line(colour = "gray88", linetype = "solid"))

exp1_rt_exposure_plot
```

### Accuracy on test trials 

First we aggregate for both unfiltered and filtered data. 

```{r expt1 acc test}
ms_test_expt1 <- df_test_expt1  %>%
    group_by(condition, intervalNum, numPic, trialType) %>%
    summarise(accuracy = mean(correct),
              ci_low = ci.low(correct),
              ci_high = ci.high(correct),
              exclusionary_criteria = "Trial Level")

ms_test_filt_expt1 <- df_test_expt1_filt  %>%
    group_by(condition, intervalNum, numPic, trialType) %>%
    summarise(accuracy = mean(correct),
              ci_low = ci.low(correct),
              ci_high = ci.high(correct),
              exclusionary_criteria = "Subject and Trial level")

ms_test_all_expt1 <- rbind(ms_test_expt1, ms_test_filt_expt1)
```

Now we plot the both the means on test trials.

```{r expt1 acc test plot revalue, echo=F}
ms_test_expt1$condition <- revalue(ms_test_expt1$condition,
                                   c("No-Social" = "No-Gaze","Social" = "Gaze"))
```

```{r expt1 acc test plot, echo=F}
expt1.acc.test <- ggplot(data=ms_test_expt1, 
                         aes(x=intervalNum, y=accuracy, 
                             colour = condition, lineType = trialType)) + 
    geom_point(size=5) +
    geom_smooth(method="lm", se =F) +
    geom_linerange(aes(ymin=accuracy - ci_low, 
                       ymax=accuracy + ci_high), width = .05, size=1) +
    #geom_line(aes(linetype = trialType), size=0.4) +
    geom_hline(aes(yintercept=1/numPic), linetype = "dashed") +
    scale_x_continuous(limits=c(-.9,8), breaks=c(0, 1, 3, 7)) +
    scale_y_continuous(limits=c(0,1)) +
    #scale_colour_grey(start = 0.3, end = 0.6) +
    scale_colour_manual(values=c("#2c7fb8", "#e34a33")) +
    facet_grid(. ~ numPic, labeller = mf_labeller) + 
    xlab("Interval Between Exposure and Test") + 
    ylab("Proportion Correct") +
    labs(colour = "Condition") +
    labs(linetype = "Trial Type") +
    guides(linetype=FALSE) +
    theme(axis.title.x = element_text(colour="black",size=22,
                                      angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.text.x = element_text(colour="grey20",size=18,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.text.y = element_text(colour="grey20",size=18,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.title.y = element_text(colour="black",size=22,face="plain"),
          legend.position=c(0.08,0.2),
          legend.text = element_text(size=18),
          legend.title = element_text(size=20, face="bold"),
          strip.text = element_text(size=16),
          panel.grid.minor = element_blank(),
          panel.grid.major = element_line(colour = "gray88", linetype = "solid"))

expt1.acc.test

grid.arrange(exp1_rt_exposure_plot, expt1.acc.test, ncol=1)
```

### LMERs

#### Predicting RT on exposure trials.

```{r expt1 lmer rt}
m1_rt_expt1 <- lmer(rt_exposure ~ condition * log2(intervalNum + 1) * log2(numPicN) + 
                        (1|subids), data=df_expo_expt1_analysis)
```

#### Predict accuracy on test trials.

```{r expt1 lmer acc test}
# 2-way model
m1_2way_expt1 <- glmer(correct ~ (trialType + condition + 
                                      log2(intervalNum + 1) + log2(numPicN))^2 + 
                           (trialType | subids), 
                       data=df_test_expt1_filt, family=binomial, nAGQ=0)

# 3-way model
m1_3way_expt1 <- glmer(correct ~ (trialType + condition + 
                                      log2(intervalNum + 1) + log2(numPicN))^3 + 
                           (trialType | subids), 
                       data=df_test_expt1_filt, family=binomial, nAGQ=0)

# 4-way model
m1_4way_expt1 <- glmer(correct ~ (trialType + condition + 
                                      log2(intervalNum + 1) + log2(numPicN))^4 + 
                           (trialType | subids), 
                       data=df_test_expt1_filt, family=binomial, nAGQ=0)

# model comparison
model_comp <- anova( m1_2way_expt1, m1_3way_expt1, m1_4way_expt1)

pandoc.table(model_comp, style="rmarkdown")
```

3-way model is best based on model comparison.

#### Compare the 3-way model for filtered and unfiltered data.

```{r expt1 lmer filter comparison}
# 2-way model unfiltered
m1_2way_expt1_unfilt <- glmer(correct ~ (trialType + condition + 
                                             log2(intervalNum + 1) + log2(numPicN))^2 + 
                                  (trialType | subids), 
                              data=df_test_expt1, family=binomial, nAGQ=0)

# 3-way model unfiltered
m1_3way_expt1_unfilt <- glmer(correct ~ (trialType + condition + 
                                             log2(intervalNum + 1) + log2(numPicN))^3 + 
                                  (trialType | subids), 
                              data=df_test_expt1, family=binomial, nAGQ=0)
```

## Experiment 2: Replication with ecologically valid stimulus set

In Experiment 2, we chose a subset of the referent/interval conditions: 
numPic = 4, and interval = 0 and 3.

Get the number of subjects in each condition.

```{r expt2 nsubs}
df_expt2 %>% 
    group_by(condition, interval) %>%
    summarise(n_subs = n_distinct(subids))
```

### Minor data cleaning, variable creation, and filters

Create variable to track experiment block.

```{r expt2 block variable}
df_expt2 %<>% mutate(block = ifelse(itemNum <= 7, "first","second"))
```

Flag trials with extremely slow or fast RTs (+/- 2SD).

```{r expt2 clean RTs}
df_expt2 %<>%
    filter(rt > 0) %>% 
    mutate(include_good_rt = ifelse(log(rt) > mean(log(rt)) + 2 * sd(log(rt)) |
                                        log(rt) < mean(log(rt)) - 2 * sd(log(rt)),
                                    "exclude", "include"))
```

### Flag social vs. no-social trials

Create a variable to track the condition for each trial.

```{r expt2 flag trial type}
df_expt2 %<>%
    mutate(condition_trial = ifelse(condition == "No-socialFirst" 
                                    & itemNum <= 7, "no-social", 
                                    ifelse(condition == "SocialFirst" 
                                           & itemNum <= 7, "social", 
                                           ifelse(condition == "No-socialFirst" 
                                                  & itemNum >= 8, "social",
                                                  ifelse(condition == "SocialFirst" 
                                                         & itemNum >= 8, 
                                                         "no-social", NA)))))
```

### Flag subs who got < 25% of exposure trials correct. 

```{r expt2 flag subs <25% correct on exposure}
ss_exposure <- df_expt2 %>%
    filter(trial_cat == "exposure" & condition_trial == "social") %>%
    group_by(subids) %>%
    summarise(mean_acc_exp = mean(correct))

# Merge mean acc with the rest of the dataset.
df_expt2 %<>% left_join(y = ss_exposure, by = "subids")
```

### Flag test trials on which subject chose target of gaze on exposure 

```{r expt2 flag test trials chose gaze target}
df_expt2 %<>%
    filter(trial_cat == "exposure") %>%
    mutate(correct_exposure = faceIdx == chosenIdx,
           rt_exposure = rt) %>%
    select(subids, itemNum, correct_exposure, rt_exposure) %>%
    left_join(x = df_expt2, y = ., by = c("subids", "itemNum"))
```

### Set up filters

Exposure trials.

```{r expt2 expo filters}
# just RT filter
df_expo_expt2 <- filter(df_expt2,
                        include_good_rt == "include",
                        condition_trial == "social",
                        trial_cat == "exposure")

# RT, subject level and trial level filter 
df_expo_expt2_filt <- filter(df_expt2,
                             trial_cat == "exposure",
                             condition_trial == "social" & mean_acc_exp > 0.25,
                             include_good_rt == "include")

# filter that gets both social/no-social trials
df_expo_expt2_analysis <- df_expt2 %>%
    filter(trial_cat == "exposure",
           mean_acc_exp > 0.25,
           correct_exposure = T | condition_trial == "no-social",
           include_good_rt == "include")
```

Get the number of subjects filtered out by the subject level filter.

```{r expt2 nsubs filtered}
df_n_expt2 <- df_expo_expt2 %>%
    group_by(condition) %>%
    summarise(n_subs = n_distinct(subids))

df_n_expt2_filt <- df_expo_expt2_filt %>%
    group_by(condition) %>%
    summarise(n_subs_filt = n_distinct(subids)) %>%
    select(n_subs_filt)

nsubs_expt2 <- cbind(df_n_expt2, df_n_expt2_filt)

nsubs_expt2
```

Test trial filters.

```{r expt2 test filters}
# just RT filter
df_test_expt2 <- df_expt2 %>%
    filter(trial_cat == "test",
           include_good_rt == "include")

# RT, subject level and trial level filter 
df_test_expt2_filt <- df_expt2 %>%
    filter(trial_cat == "test",
           mean_acc_exp > 0.25 ,
           include_good_rt == "include",
           correct_exposure == T | condition_trial == "no-social")
```

Save final, cleaned analysis dataset for manuscript.

```{r save final dataset expt2}
df_expt2_analysis_final <- df_test_expt2_filt %>% 
    dplyr::bind_rows(df_expo_expt2_analysis) %>% 
    dplyr::arrange(subids) 

write.csv(x = df_expt2_analysis_final, 
          "../../paper/manuscript/soc-xsit-expt2-finalData.csv",
          row.names = F)
```

### Analyze Exposure Trials

Accuracy, selecting target of gaze.

```{r expt2 acc expo}
# unfiltered
ms_expo_expt2 <- df_expo_expt2 %>%
    group_by(intervalNum) %>%
    summarise(accuracy_exposure = mean(correct),
              ci_low = ci.low(correct),
              ci_high = ci.high(correct)) %>%
    mutate(filter = "Unfiltered")

# filtered
ms_expo_expt2_filt <- df_expo_expt2_filt %>%
    group_by(intervalNum) %>%
    summarise(accuracy_exposure = mean(correct),
              ci_low = ci.low(correct),
              ci_high = ci.high(correct)) %>%
    mutate(filter = "Filtered")

ms_expo_all_expt2 <- rbind(ms_expo_expt2, ms_expo_expt2_filt)
```

Now plot mean correct for exposure trials for each interval.

```{r expt2 acc expo plot, echo=F}
ggplot(data=ms_expo_all_expt2, 
       aes(x=intervalNum, y=accuracy_exposure)) + 
    geom_pointrange(aes(ymin=accuracy_exposure - ci_low, 
                        ymax=accuracy_exposure + ci_high), 
                    width = .05, size=0.6) +
    geom_hline(aes(yintercept=1/4), linetype = "dashed") +
    scale_x_continuous(limits=c(-.9,4), breaks=c(0,3)) +
    scale_y_continuous(limits=c(0,1)) +
    scale_colour_manual(values=c("#1f78b4", "red")) +
    xlab("Intervening Trials") + 
    ylab("Prop. Choosing Repeated Referent") +
    labs(colour = "Condition") +
    labs(linetype = "Trial Type") +
    guides(linetype=FALSE) +
    facet_grid(~filter) +
    theme(text = element_text(size=14), 
          axis.title.y=element_text(vjust=1),
          axis.title.x=element_text(vjust=-0.3),
          legend.justification=c(0,0),
          legend.position = c(0,0)) 
```

RT on exposure trials.

```{r expt2 rt expo}
ms_rt_expo_expt2 <- df_expo_expt2_analysis %>%
    group_by(condition_trial, intervalNum) %>%
    summarise(rt_exposure = mean(rt),
              ci_low = ci.low(rt),
              ci_high = ci.high(rt))
```

Plot RT differences

```{r expt2 rt expo plot, echo=F}
# revalue social/no-social --> gaze/no-gaze
ms_rt_expo_expt2$condition <- revalue(ms_rt_expo_expt2$condition,
                                      c("no-social" = "No-Gaze", "social" = "Gaze"))

expt2.rt.expo <- ggplot(data=ms_rt_expo_expt2, 
                        aes(x=intervalNum, y=rt_exposure, color = condition)) + 
    geom_pointrange(aes(ymin=rt_exposure - ci_low, 
                        ymax=rt_exposure + ci_high), width = .05, size=1.5) +
    scale_x_continuous(limits=c(-.9,4), breaks=c(0,3)) +
    geom_smooth(method="lm", se=F) +
    scale_y_continuous(limits=c(0,5000)) +
    scale_colour_manual(values=c("#e34a33", "#2c7fb8")) +
    #scale_color_grey(start = 0.3, end = 0.6) + 
    xlab("Intervening Trials") + 
    ylab("Response Time (ms)") +
    labs(colour = "Condition") +
    labs(linetype = "Trial Type") +
    ggtitle("Study Time on Exposure Trials") + 
    #guides(linetype=FALSE, color=F) +
    theme(axis.title.x = element_text(colour="black",size=22,
                                      angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.text.x = element_text(colour="grey20",size=18,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.text.y = element_text(colour="grey20",size=18,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.title.y = element_text(colour="black",size=22,face="plain"),
          #legend.position=c(0.82,0.80),
          legend.text = element_text(size=20),
          legend.title = element_text(size=22, face="bold"),
          plot.title = element_text(lineheight=1, face="bold", size = 24),
          strip.text = element_text(size=16))

expt2.rt.expo

# save output
# ggsave("exp2-rt-expo.pdf", expt2.rt.expo, width=6, height=5)
```

## Analyze test trials

Get means and CIs for each condition.

```{r expt2 acc test aggregate}
# unfiltered
ms_test_expt2 <- df_test_expt2 %>%
    group_by(trialType, condition_trial, intervalNum) %>%
    summarise(accuracy = mean(correct),
              ci_low = ci.low(correct),
              ci_high = ci.high(correct)) %>%
    mutate(filter = "Unfiltered")

# filtered (subject level)
ms_test_expt2_filt <- df_test_expt2_filt %>%
    group_by(trialType, condition_trial, intervalNum) %>%
    summarise(accuracy = mean(correct),
              ci_low = ci.low(correct),
              ci_high = ci.high(correct)) %>%
    mutate(filter = "Filtered")

ms_test_all_expt2 <- rbind(ms_test_expt2, ms_test_expt2_filt)
```

Now plot accuracy for test trials.

```{r expt2 acc test plot, echo=F}
# revalue social/no-social --> gaze/no-gaze
ms_test_expt2_filt$condition_trial <- revalue(ms_test_expt2_filt$condition_trial,
                                              c("no-social" = "No-Gaze", "social" = "Gaze"))

expt2.acc.test <- ggplot(data=ms_test_expt2_filt, 
                         aes(x=intervalNum, y=accuracy, 
                             colour = condition_trial)) + 
    geom_line(aes(linetype = trialType), size=0.6) +
    geom_pointrange(aes(ymin=accuracy - ci_low, 
                        ymax=accuracy + ci_high), 
                    width = .05, size=1.5) +
    geom_hline(aes(yintercept=1/4), linetype = "dashed") +
    scale_x_continuous(limits=c(-.9,4), breaks=c(0, 3)) +
    scale_y_continuous(limits=c(0,1)) +
    scale_colour_manual(values=c("#e34a33", "#2c7fb8")) +
    #scale_colour_grey(start=0.6, end=0.3) +
    xlab("Intervening Trials") + 
    ylab("Proportion Correct") +
    labs(colour = "Condition") +
    labs(linetype = "Trial Type") +
    guides(linetype=FALSE) +
    ggtitle("Accuracy on Test Trials") +
    theme(axis.title.x = element_text(colour="black",size=22,
                                      angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.text.x = element_text(colour="grey20",size=18,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.text.y = element_text(colour="grey20",size=18,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.title.y = element_text(colour="black",size=22,face="plain"),
          #legend.position=c(0.80,0.88),
          legend.text = element_text(size=20),
          legend.title = element_text(size=22, face="bold"),
          plot.title = element_text(lineheight=1, face="bold", size = 24),
          strip.text = element_text(size=16))

expt2.acc.test

grid.arrange(expt2.rt.expo, expt2.acc.test, ncol=2)
```

### LMERs 

Predicting RT on exposure trials.

```{r expt2 lmer rt}
m1_rt_expt2 <- lmer(rt ~ condition_trial * log2(intervalNum + 1) + 
                        (1|subids), data=df_expo_expt2_analysis)
```

Comparing models with different levels of complexity.

```{r expt 2 lmers model comparison}
# filtered 2-way
m1_expt2_2way_filt <- glmer(correct ~ (trialType + condition_trial + intervalNum)^2 + 
                                (trialType | subids), nAGQ=0,
                            data = df_test_expt2_filt,
                            family=binomial)

# filtered 3-way
m1_expt2_3_way_filt <- glmer(correct ~ (trialType + condition_trial + intervalNum)^3 + 
                                 (trialType | subids), nAGQ=0,
                             data = df_test_expt2_filt,
                             family=binomial)

model_comp_expt2 <- anova(m1_expt2_2way_filt, m1_expt2_3_way_filt)

pandoc.table(model_comp_expt2, style="rmarkdown")
```

3-way is no better than the 2-way.

### LMERs comparing filtered vs. unfiltered data.

```{r expt2 lmers filters}
# unfilt 2-way
m1_expt2_unfilt <- glmer(correct ~ (trialType + condition_trial + intervalNum)^2 + 
                             (trialType | subids), nAGQ=0,
                         data = df_test_expt2,
                         family=binomial)

# filtered 2-way
m1_expt2_filt <- glmer(correct ~ (trialType + condition_trial + intervalNum)^2 + 
                           (trialType | subids), nAGQ=0,
                       data = df_test_expt2_filt,
                       family=binomial)
```

Model output is no different when we use the filtered data.

## Experiment 3: Parametric reliability manipulation

Minor data cleaning and variable creation.

```{r expt3 data cleaning}
# create clean reliablity variable
df_expt3$prop_cond_clean <- revalue(df_expt3$condition,
                                    c("0%_reliable" = "0%",
                                      "25%_reliable" = "25%",
                                      "50%_reliable" = "50%",
                                      "75%_reliable" = "75%",
                                      "100%_reliable" = "100%"))

# change order of condition factor for plotting
df_expt3$prop_cond_clean <- factor(df_expt3$prop_cond_clean,
                                   levels = c("0%", "25%", "50%", "75%", "100%"))

# Create continuous variable for reliability
df_expt3$reliability[df_expt3$prop_cond_clean=="0%"] <- .00
df_expt3$reliability[df_expt3$prop_cond_clean=="25%"] <- .25
df_expt3$reliability[df_expt3$prop_cond_clean=="50%"] <- .50
df_expt3$reliability[df_expt3$prop_cond_clean=="75%"] <- .75
df_expt3$reliability[df_expt3$prop_cond_clean=="100%"] <- 1.00
```

### Get the number of subjects in each experiment and condition.

```{r expt3 get number of subs}
df_expt3 %>%
    group_by(prop_cond_clean, experiment) %>%
    summarise(n_subs = n_distinct(subids))
```

### Clean up RTs.

```{r expt3 clean RTs}
df_expt3 <- df_expt3 %>%
    filter(rt > 0) %>% 
    mutate(include_good_rt = ifelse(log(rt) > mean(log(rt)) + 2 * sd(log(rt)) | 
                                        log(rt) < mean(log(rt)) - 2 * sd(log(rt)),
                                    "exclude", "include"))
```

Flag whether participant chose the target of eye gaze on exposure trials in the test block.

```{r expt3 chose gaze target on exposure trials test block}
df_expt3 %<>% 
    filter(trial_category == "exposure", block == "test") %>% 
    select(subids, 
           gaze_target_exposure = gaze_target, 
           chosen_exposure = chosen, 
           correct_exposure = correct, 
           itemNum,
           experiment) %>% 
    left_join(x = df_expt3, by = c("subids", "itemNum", "experiment"))
```

### Analyze Familiarization Block

RT on exposure trials.

```{r expt3 rt exposure trials fam block}
ms_rt_expo_fam <- df_expt3 %>%
    filter(trial_category == "exposure", block == "familiarization", 
           include_good_rt == "include") %>% 
    group_by(prop_cond_clean, experiment) %>%
    summarise(rt_exposure = mean(rt),
              ci_low = ci.low(rt),
              ci_high = ci.high(rt))

ggplot(ms_rt_expo_fam, 
       aes(x=prop_cond_clean, y=rt_exposure)) +
    geom_pointrange(aes(ymin=rt_exposure - ci_low,
                        ymax=rt_exposure + ci_high), 
                    width = .1, size = 0.8) + 
    scale_y_continuous(limits=c(500,4500)) +
    ylab("Response Time (ms)") +
    xlab("Level of Reliability") +
    facet_grid(. ~ experiment) +
    theme(text = element_text(size=16),
          axis.text.x  = element_text(angle=0, vjust=0.5, size=12))
```

Accuracy on test trials in familiarization block

```{r expt3 acc test trials familiarization block}
ms_test_fam <- df_expt3 %>%
    filter(trial_category == "test", block == "familiarization", 
           include_good_rt == "include") %>% 
    group_by(prop_cond_clean, trialType, experiment) %>%
    summarise(accuracy = mean(correct),
              ci_low = ci.low(correct),
              ci_high = ci.high(correct))

ggplot(ms_test_fam, 
       aes(x=prop_cond_clean, y=accuracy, 
           group=trialType, colour=trialType)) +
    geom_pointrange(aes(ymin=accuracy - ci_low,
                        ymax=accuracy + ci_high), 
                    width = .1, size=0.7) +
    geom_hline(yintercept=0.5, linetype = "dashed") +
    scale_y_continuous(limits=c(0,1)) + 
    geom_smooth(method='lm') +
    facet_grid(. ~ experiment) +
    ggtitle("Accuracy on Test Trials in Familiarization Block")
```

Split this by first and second half. 

```{r expt3 acc test trials familiarization block split}
ms_test_fam_blocked <- df_expt3 %>%
    filter(trial_category == "test", block == "familiarization", 
           include_good_rt == "include") %>% 
    mutate(second_half = ifelse(itemNum > 3, "First Block", "Second Block")) %>%
    group_by(prop_cond_clean, trialType, second_half, experiment) %>%
    summarise(accuracy = mean(correct),
              ci_low = ci.low(correct),
              ci_high = ci.high(correct))
```

Plot. 

```{r}
ggplot(ms_test_fam_blocked, 
       aes(x=prop_cond_clean, y=accuracy, 
           group=trialType, colour=trialType)) +
    geom_pointrange(aes(ymin=accuracy - ci_low,
                        ymax=accuracy + ci_high), 
                    width = .1, size=0.7) +
    geom_hline(yintercept=0.5, linetype = "dashed") +
    scale_y_continuous(limits=c(0,1)) + 
    geom_smooth(method='lm') +
    facet_grid(experiment ~ second_half) + 
    ggtitle("Accuracy on Test Trials in Familiarization Block")
```

#### Analyze performance on test block

Anayze RT on exposure trials in the test block.

```{r expt3 rt exposure trials test block}
ms_rt_expo_test <- df_expt3 %>%
    filter(trial_category == "exposure", block == "test", 
           include_good_rt == "include") %>% 
    group_by(prop_cond_clean, trialType, experiment) %>%
    summarise(rt_exposure = mean(rt),
              ci_low = ci.low(rt),
              ci_high = ci.high(rt))
```

Plot. 

```{r}
ggplot(ms_rt_expo_test, 
       aes(x=prop_cond_clean, y=rt_exposure, color = trialType)) +
    geom_pointrange(aes(ymin=rt_exposure - ci_low,
                        ymax=rt_exposure + ci_high), 
                    width = .1, size = 0.8) + 
    scale_y_continuous(limits=c(500,4500)) +
    ylab("Response Time (ms)") +
    xlab("Condition") +
    facet_grid(. ~ experiment) +
    theme(text = element_text(size=14))
```

Accuracy on familiarization trials in test block

```{r expt3 acc fam trials in test block}
ms_expo_test <- df_expt3 %>%
        filter(trial_category == "test", block == "test", 
           include_good_rt == "include", experiment == "replication") %>% 
    group_by(prop_cond_clean) %>%
    summarise(accuracy = mean(correct_exposure, na.rm=T),
              ci_low = ci.low(correct_exposure),
              ci_high = ci.high(correct_exposure),
              mean_rel = mean(rel_subj, na.rm=T),
              ci_low_rel = ci.low(rel_subj),
              ci_high_rel = ci.high(rel_subj)
              )
```

Now plot chose target of gaze

```{r chose gaze target plot}
expt3_chose_gazetar_plot <- ggplot(ms_expo_test, 
                                   aes(x=prop_cond_clean, y=accuracy, group=1)) +
    geom_smooth(method="lm", se=F, color="black") +
    geom_pointrange(aes(ymin=accuracy - ci_low,
                        ymax=accuracy + ci_high), width = .05, size=1, color = "black") +
    geom_hline(yintercept=0.25, linetype = "dashed") +
    scale_y_continuous(limits=c(0,1)) +
    xlab("Level of Reliablity") + 
    ylab("Prop. Chose Target of Gaze") + 
    theme(axis.title.x = element_text(colour="black",size=16,
                                      angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.title.y = element_text(colour="black",size=16,
                                      angle=90,hjust=0.5,vjust=0.5,face="plain"),
          axis.text.x = element_text(colour="grey20",size=12,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.text.y = element_text(colour="grey20",size=12,
                                     angle=0,hjust=0.5,vjust=0,face="plain"))

expt3_chose_gazetar_plot
```

Accuracy on test trials in the test block

```{r expt3 acc on test trials test block}
ms_test_test <- df_expt3 %>%
    filter(trial_category == "test", block == "test", 
           include_good_rt == "include") %>% 
    group_by(prop_cond_clean, trialType) %>%
    summarise(accuracy = mean(correct),
              ci_low = ci.low(correct),
              ci_high = ci.high(correct))
```

Now plot.

```{r expt3 acc test expt 3 cogsci plot, echo=F}
expt3_acc_test <- ggplot(data=ms_test_test, 
                         aes(x=prop_cond_clean, y=accuracy, group=trialType,
                             color=trialType, label = trialType)) + 
    geom_pointrange(aes(ymin=accuracy - ci_low, 
                        ymax=accuracy + ci_high), 
                    width = .05, size=1) +
    geom_smooth(method='lm', se=F) +
    geom_hline(aes(yintercept=1/4), linetype = "dashed") +
    scale_y_continuous(limits=c(0,1)) +
    # scale_colour_grey(start=0.3, end=0.6) +
    scale_colour_manual(values=c("#2c7fb8", "#e34a33")) +
    xlab("Reliability of Gaze") + 
    ylab("Proportion Correct") +
    labs(color = "Trial Type") +
    guides(color=FALSE) +
    theme(axis.title.x = element_text(colour="black",size=18,
                                      angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.title.y = element_text(colour="black",size=18,
                                      angle=90,hjust=0.5,vjust=0.8,face="plain"),
          axis.text.x = element_text(colour="grey20",size=12,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.text.y = element_text(colour="grey20",size=12,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          legend.text = element_text(size=13),
          legend.title = element_text(size=13, face="bold")) 

expt3_acc_test

# save output
# ggsave("exp3-acc-test.pdf", expt3_acc_test, width=7.8, height=4.5)
```

Analyze subject reported reliablity

```{r subjective reliablity analysis 1}
ms_test_subj_rel <- df_expt3 %>%
    filter(experiment == "replication") %>% 
    mutate(rel_subj = as.numeric(as.character(rel_subj))) %>% 
    group_by(prop_cond_clean) %>%
    summarise(subjective_reliability = mean(rel_subj, na.rm=T),
              ci_low = ci.low(rel_subj),
              ci_high = ci.high(rel_subj))

qplot(x=prop_cond_clean, y=subjective_reliability, group=1, data=ms_test_subj_rel) + 
    ylim(c(0,1)) +
    geom_smooth(method="lm", se=T)
```

Histogram. 

```{r}
# get the total number of correct for each sub on exposure trials in test block
df_expt3 %<>%
    filter(trial_category == "exposure",
           block == "test", include_good_rt == "include") %>% 
    group_by(subids, experiment) %>% 
    summarise(total_exposure_correct = sum(correct_exposure))  %>% 
    left_join(x = df_expt3, by = c("subids", "experiment"))

# get mean accuracy on each trialt type for each sub
df_expt3 %<>%
    filter(trial_category == "test",
           block == "test", include_good_rt == "include") %>% 
    group_by(subids, experiment, trialType) %>% 
    summarise(sub_mean_accuracy = mean(correct))  %>% 
    spread(key = trialType, value = sub_mean_accuracy) %>% 
    rename(same_accuracy = Same, switch_accuracy = Switch) %>% 
    left_join(x = df_expt3, by = c("subids", "experiment"))

mss_subj_rel <- df_expt3 %>% 
    filter(experiment == "replication") %>% 
    select(subids, rel_subj, prop_cond_clean, total_exposure_correct, 
           same_accuracy, switch_accuracy, experiment) %>% 
    distinct()
```

Plot

```{r}
qplot(rel_subj, facets=.~prop_cond_clean, 
      data=mss_subj_rel, binwidth = 0.1)
```

Reported reliability vs. number correct on exposure - individual consistency.

```{r subjective reliablity analysis 2}
qplot(total_exposure_correct, rel_subj, col = prop_cond_clean, 
      data=mss_subj_rel) + geom_smooth(method="lm", se=FALSE)
```

Reported reliability vs. number correct on exposure - means.

```{r subjective reliablity analysis}
ms_test_subj_rel <- df_expt3 %>%
    filter(experiment == "replication", include_good_rt == "include") %>% 
    group_by(prop_cond_clean, total_exposure_correct) %>%
    summarise(subj = mean(rel_subj, na.rm=TRUE), 
              cih = ci.high(rel_subj),
              cil = ci.low(rel_subj))
```

Now plot

```{r expt3 subj rel plot}
expt3_subj_rel_plot <- qplot(total_exposure_correct, subj, col = prop_cond_clean, 
                             ymin = subj - cil, ymax = subj + cih,
                             geom="pointrange",
                             position=position_dodge(width=.1),
                             data=ms_test_subj_rel, ylab="Subjective reliability", 
                             xlab="Num Trials Chose Gaze Target") + 
    geom_smooth(method="lm", se=FALSE) +
    scale_color_discrete(name="Reliability Level") +
    theme(axis.title.x = element_text(colour="black",size=16,
                                      angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.title.y = element_text(colour="black",size=16,
                                      angle=90,hjust=0.5,vjust=0.5,face="plain"),
          axis.text.x = element_text(colour="grey20",size=12,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.text.y = element_text(colour="grey20",size=12,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          legend.text = element_text(size=13),
          legend.title = element_text(size=13, face="bold"))

expt3_subj_rel_plot 

# save output
# ggsave("expt3-subj-rel-chose-gaze-target.pdf", expt3_subj_rel_plot, width=7, height=4)
```

Relationship between subjective accuracy, reliablity condition, and test trial performance

```{r}
gather_mss_rel_subj <- mss_subj_rel %>% 
    gather(key = trialType, value = sub_mean_accuracy, 5:6) %>% 
    arrange(subids)
## 3 way interaction plot
qplot(x = sub_mean_accuracy, y = rel_subj, data = gather_mss_rel_subj) +
    facet_grid(prop_cond_clean ~ trialType) +
    geom_smooth(method = "lm")
```

### LMERs

## Accuracy on exposure trials in test block.

```{r expt3 lmer acc expo test block}
m1_expo_expt3 <- glmer(correct ~ reliability + (1 | subids),
                       data = filter(df_expt3, trial_category == "exposure", block == "test",
                                     experiment == "replication", include_good_rt == "include"),
                       nAGQ = 10,
                       control = glmerControl(optimizer = "bobyqa"),
                       family = binomial)

knitr::kable(summary(m1_expo_expt3)$coef, digits = 3)
```

Participants are more likely to select the target of gaze when the gaze cue is more reliable.

## Predict gaze following based on subjective reliability judgments.

```{r}
m1_subj_rel_expt3 <- glm(correct ~ rel_subj,
                       data = filter(df_expt3, trial_category == "exposure", block == "test",
                                     experiment == "replication", include_good_rt == "include"),
                       family = binomial)

knitr::kable(summary(m1_subj_rel_expt3)$coef, digts = 3)
```

Participants who rate the cue as more reliable are alos more likely to use the cue

## Accuracy on test trials in test block.

```{r expt3 lmers}
# reliablity as factor, linear interaction
m1_test_expt3 <- glmer(correct ~ trialType * prop_cond_clean + (trialType | subids),
                       data = filter(df_expt3, trial_category == "test", block == "test",
                                     experiment == "replication", include_good_rt == "include"),
                       control = glmerControl(optimizer = "bobyqa"),
                       nAGQ = 1,
                       family = binomial)

summary(m1_test_expt3)
```

```{r}
m1_noslope_expt3 <- glmer(correct ~ trialType * prop_cond_clean + (1 | subids),
                    data = filter(df_expt3, trial_category == "test", block == "test",
                                     experiment == "replication", include_good_rt == "include"),
                    control = glmerControl(optimizer = "bobyqa"),
                    nAGQ = 1,
                    family = binomial)

summary(m1_noslope_expt3)
```

Anova comparing the random intercept to the random slope and random intercept model.

```{r}
anova(m1_noslope_expt3, m1_test_expt3)
```

Model with both random slopes and intercepts is better. 

## Reliablity as continuous 

```{r expt3 lmer rel as continuous}
m2_expt3 <- glmer(correct ~ trialType * reliability + (trialType | subids),
                  data = filter(df_expt3, trial_category == "test", block == "test",
                                     experiment == "replication", include_good_rt == "include"),
                  control = glmerControl(optimizer = "bobyqa"),
                  nAGQ = 1,
                  family = binomial)

summary(m2_expt3)
```

```{r}
m2_noslope_expt3 <- glmer(correct ~ trialType * reliability + (1 | subids),
                          data = filter(df_expt3, trial_category == "test", block == "test",
                                     experiment == "replication", include_good_rt == "include"),
                          control = glmerControl(optimizer = "bobyqa"),
                          nAGQ = 1,
                          family = binomial)

summary(m2_noslope_expt3)
```

Nested model comparison.

```{r}
anova(m2_noslope_expt3, m2_expt3)
```

Random slopes and intercept model is better. 

## Aggregate subject level then model

```{r}
mss_expt3 <- df_expt3 %>%
    filter(trial_category == "test", block == "test",
           experiment == "replication", include_good_rt == "include") %>% 
    group_by(subids, trialType, reliability) %>%
    summarize(correct = mean(correct))

# now model
m2_lmer_expt3 <- lmer(correct ~ trialType * reliability + (1 | subids), 
                     data = mss_expt3)

summary(m2_lmer_expt3)
```

#### Predict test performance from selecting target of gaze on exposure trials

Now model. 

```{r}
m4_expt3 <- glmer(correct ~ total_exposure_correct * trialType + (trialType | subids),
                  control = glmerControl(optimizer = "bobyqa"),
                  data = filter(df_expt3, trial_category == "test", block == "test",
                                experiment == "replication", include_good_rt == "include"),
                  nAGQ = 1,
                  family = binomial)
summary(m4_expt3)
```

Now we plot the new analysis: accuracy on test trials as a function of 
accuracy on exposure trials (selecting the gaze target).

```{r expt3 acc test by acc exposure plot, echo=F}
ms_acc_exp_test_expt3 <- df_expt3 %>%
    filter(trial_category == "test", block == "test",
           include_good_rt == "include", experiment == "replication") %>% 
    group_by(trialType, total_exposure_correct) %>%
    summarise(cih = ci.high(correct), 
              cil= ci.low(correct),
              correct = mean(correct))
```

Plot

```{r expt3 chose gazetar analysis}
expt3_acc_test_chose_gazetar <- ggplot(data=ms_acc_exp_test_expt3, 
                                       aes(x=total_exposure_correct, y=correct, group=trialType,
                                           color=trialType, label = trialType)) + 
    geom_pointrange(aes(ymin=correct - cil, 
                        ymax=correct + cih), 
                    width = .05, size=1) +
    geom_smooth(method='lm', se=F) +
    geom_hline(aes(yintercept=1/4), linetype = "dashed") +
    scale_x_continuous(limits=c(0,8), breaks=c(0:8)) +
    scale_y_continuous(limits=c(0,1)) +
    #scale_colour_grey(start=0.3, end=0.6) +
    scale_colour_manual(values=c("#2c7fb8", "#e34a33")) +
    xlab("Gaze Following on Exposure Trials") + 
    ylab("Proportion Correct") +
    labs(color = "Trial Type") +
    guides(color=FALSE) +
    theme(axis.title.x = element_text(colour="black",size=18,
                                      angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.title.y = element_text(colour="black",size=18,
                                      angle=90,hjust=0.5,vjust=0.8,face="plain"),
          axis.text.x = element_text(colour="grey20",size=12,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.text.y = element_text(colour="grey20",size=12,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          legend.text = element_text(size=13),
          legend.title = element_text(size=13, face="bold")) 


gridExtra::grid.arrange(expt3_acc_test, expt3_acc_test_chose_gazetar, ncol = 2)

#ggsave("expt3-acc-test-chosegazetar.pdf", expt3_acc_test_chose_gazetar, width=7.5, height=5)
```

Save final, clean dataset for experiment 3 for manuscript.

```{r}
write.csv(x = df_expt3, 
          "../../paper/manuscript/soc-xsit-expt3-finalData.csv",
          row.names = F)
```
