---
title: "soc-xsit-v2-looks-munging"
author: "Kyle MacDonald"
date: "September 25, 2014"
output: html_document
---

This script munges, merges, and saves a tidy file, which has all the raw data from different versions of soc-xsit-v2 experiments. 

Load libraries 

```{r libraries}
library(plyr)
library(dplyr)
source("/Users/kmacdonald/Documents/Projects/SOC_XSIT/XSIT-MIN/analysis/Ranalysis/useful.R")
```


#### Read in data. 
- d: manipulated gaze length, 4-referents, 0 delay
- d1: ran the short gaze in social and no-social condition
- d2: replicate expt 2 using a within-subjects design
- d3: manipulated the language cue during exposure ("this" vs. "one"), eye gaze in both
- d4: aggregated data from FYP experiment

```{r read data}
#set path for reading data
read_path <- file.path("/Users", "kmacdonald", "Documents", 
                       "Projects", "SOC_XSIT", "processed_data", 
                       "adult-looks/")

read_path_fyp <- file.path("/Users", "kmacdonald", "Documents", 
                       "Projects", "SOC_XSIT", "processed_data", 
                       "adult-fyp/")

d <- tbl_df(read.csv(paste(read_path, 
                           "soc_xsit_looks_pilot.csv", sep="")))
d1 <- tbl_df(read.csv(paste(read_path, 
                            "soc_xsit_looks_pilot_2.csv", sep="")))
d2 <- tbl_df(read.csv(paste(read_path, 
                            "soc_xsit_looks_pilot_3_withinsubs.csv", sep="")))
d3 <- tbl_df(read.csv(paste(read_path, 
                            "soc_xsit_looks_pilot_4_thisone_btw.csv", sep="")))
d4 <- tbl_df(read.csv(paste(read_path_fyp,
                            "aggregate_soc_xsit.csv", sep="")))
```

#### Merge data sets, tracking experiment version. 

```{r merge datasets}
#remove samepos and random "X" column from d/d1
#rename example, exposure, and test columns in d/d1
d <- d %>%
        select(-X, -samePos, 
               example_trial = exampleTrial, 
               exposure_trial = exposureTrial,
               test_trial = testTrial,
               matches("."))

d1 <- d1 %>%
        select(-X, -samePos, 
               example_trial = exampleTrial, 
               exposure_trial = exposureTrial,
               test_trial = testTrial,
               matches("."))

#add experiment tracking variable to each data frame
d <- mutate(d, experiment = "look_length")
d1 <- mutate(d1, experiment = "soc_vs_no_soc_btw")
d2 <- mutate(d2, experiment = "soc_vs_no_soc_within")
d3 <- mutate(d3, experiment = "this_one")


# wrap in list 
d.list <- list(d, d1, d2, d3)

#join all 4 data frames
d.all_df <- ldply(.data = d.list, .fun = rbind())

#make experiment variable factor
d.all_df$experiment <- as.factor(d.all_df$experiment)

#check the number of trials for each sub
dups <- d.all_df %>%
                group_by(subid) %>%
                summarise(n_trials = n())

d.all_df <- join(d.all_df, dups)
```

Flag subs who have more trials than they should (participated more than once), 1=duplicate, 0=not-duplicate

```{r flag duplicates}

d.all_df <- mutate(d.all_df.temp, 
                        duplicate = ifelse(experiment == "this_one" & n_trials > 16, 1, 
                                          ifelse(experiment == "look_length" & n_trials > 20, 1, 
                                                ifelse(experiment=="soc_vs_no_soc_btw" & n_trials > 20, 1,
                                                      ifelse(experiment=="soc_vs_no_soc_within" & n_trials > 36, 1, 0
                                                             )))))

#anonymize subids
d.all_df <- anonymize.sids(d.all_df, "subid")

#save final data file
write.csv(d.all_df, "/Users/kmacdonald/Documents/Projects/SOC_XSIT/processed_data/adult-looks/soc_xsit_data_all.csv", row.names=F)
```

