---
title: "SOC-XSIT Data Munging"
author: "Kyle MacDonald"
date: "October 9, 2014"
output: html_document
---

This script munges, merges, and saves a tidy file, which has all the raw data from different versions of soc-xsit experiments. The main goal is to lay out all the different exclusionary criteria in one script such that we can iterate quickly between these criteria. 

Load libraries

```{r load libraries}
library(rjson)
library(plyr)
library(dplyr)
library(chron)
library(stringr)
```

#### Read in raw JSON data

Set file paths

```{r file paths}
## set file paths for reading and writing data
read_path <- file.path("/Users", "kmacdonald", "Documents", "Projects", "SOC_XSIT", "raw_data", "adult-good", "replication/")
write_path <- file.path("/Users", "kmacdonald", "Documents", "Projects", "SOC_XSIT", "processed_data", "adult-looks", "redo_processing/")
```

Read in raw data

```{r read in raw JSON data}
## gets all raw JSON files at one time
all_results <- list.files(path = read_path, pattern = '*.results', all.files = FALSE)

## creates empty data frame
all.data <- data.frame()
```

Process raw JSON data. Loop through all of the results files, grabbing relevant data from JSON, creating columns for the following: condition (soc/no_soc), number of pics each trial, interval between exposure and test. Also flags test and exposure trials.

```{r process JSON}

```

