---
title: "Soc-xsit Data Munging"
author: "Kyle MacDonald"
date: "September 17, 2015"
output: html_document
---

Clear workspace and set working directory 

```{r clear workspace, echo=F, warning=F}
rm(list=ls())
source("../analysis/useful.R")
library(pander)
library(magrittr)
library(gridExtra)
library(tidyr)
library(directlabels)
```

### Read in data from all 4 Experiments:

* Experiment 1: Large scale experiment manipulating attention and memory demands
* Experiment 2: Replication of Experiment 1 with more ecologically valid stimulus set
* Experiment 3: Parametric manipulation of cue reliablity
* Experiment 4: Manipulation of a fixed inspection time for exposure trials

```{r}
df_expt1 <- read.csv("2_raw_compiled/e1_soc_xsit_schematic.csv", stringsAsFactors = F)
df_expt2 <- read.csv("2_raw_compiled/e2_soc_xsit_live_within.csv", stringsAsFactors = F)
df_expt3 <- read.csv("2_raw_compiled/e3_soc_xsit_reliability_parametric.csv", stringsAsFactors = F)
df_expt4 <- read.csv("2_raw_compiled/e4_soc_xsit_inspection.csv", stringsAsFactors = F)
```

## Experiment 1

### Data cleaning 

```{r exp1 fix face index 6-referent condition}
# create a function to recode the face index variable in the 6-referent condition  to match the chosen index variable 
# we do this so we can know if participants selected the gaze target
convert_idx <- function(idx, numPic) {
  string_idx <- as.character(idx)
  new_idx <- ifelse(numPic != 6, idx, 
                    switch(string_idx,
                           "-1" = -1,
                           "0" = 2,
                           "1" = 3,
                           "2" = 4,
                           "3" = 5,
                           "4" = 0,
                           "5" = 1,
                           stop("Invalid entry to switch")))
  new_idx <- as.integer(new_idx)
}

# now we apply this function to each row of the data frame using rowwise()
df_expt1 %<>% 
  dplyr::rowwise() %>% 
  mutate(final_faceIdx = convert_idx(idx = faceIdx, numPic = numPicN)) %>% 
  ungroup() 
```

### Flag correct/incorrect exposure and test trials

* Correct exposure trials are defined as selecting the gaze target if you were in the Gaze condition.
* Correct test trials are defined as selecting the object that was "kept" from the exposure trial.

```{r exp1 flag correct trials}
df_expt1 %<>%
  mutate(correct = ifelse(trial_category == "test" & chosen == kept, TRUE,
                          ifelse(trial_category == "exposure" & condition == "No-Social", NA,
                                 ifelse(chosenIdx == final_faceIdx, TRUE,
                                 FALSE))))
```

#### Remove fast and slow RTs on exposure trials 

```{r expt1 score gaze following on exposure}
df_expo_expt1 <- df_expt1 %>%
  filter(trial_category == "exposure") %>% 
  select(subid, itemNum, rt, condition, correct) %>% 
  rename(correct_exposure = correct, rt_exposure = rt) %>%
  filter(rt_exposure > 0) %>% 
  mutate(include_good_rt_exposure = ifelse(log(rt_exposure) > mean(log(rt_exposure)) + 
                                             2 * sd(log(rt_exposure)) |
                                             log(rt_exposure) < mean(log(rt_exposure)) - 
                                             2 * sd(log(rt_exposure)),
                                           "exclude", "include"))

# Merge exposure trial information with full dataset
df_expt1 %<>% left_join(y = df_expo_expt1, by = c("subid", "itemNum", "condition"))
```

#### Flag subs in the social condition who performed worse than chance on exposure trials.

```{r expt 1 flag subs < 25% correct on exposure trials}
df_test_expo_correct <- df_expt1 %>%
  filter(trial_category == "test") %>%
  group_by(subid, numPic, condition) %>%
  summarise(mean_acc_exp = mean(correct)) %>%
  rowwise() %>% 
  mutate(include_expo = ifelse(condition == "No-Social", "include",
                               ifelse(mean_acc_exp > 1/numPic, "include", 
                                      "exclude"))) %>% 
  ungroup()

df_expt1 %<>% left_join(., df_test_expo_correct, by = c("subid", "condition", "numPic"))
```

#### Flag test trials with really slow or fast RTs (+/- 2SD).

```{r expt1 rt cleaning}
df_test_rt <- df_expt1 %>% 
  filter(trial_category == "test") %>% 
  rename(rt_test = rt) %>% 
  filter(rt_test > 0) %>% 
  mutate(include_good_rt_test = ifelse(log(rt_test) > mean(log(rt_test)) + 
                                         2 * sd(log(rt_test)) |
                                         log(rt_test) < mean(log(rt_test)) - 
                                         2 * sd(log(rt_test)),
                                       "exclude", "include")) %>% 
  select(subid, itemNum, include_good_rt_test)

df_expt1 %<>% left_join(y = df_test_rt, by = c("subid", "itemNum"))
```

#### Save clean Expt. 1 dataset

```{r expt1 save clean dataset, eval = F}
write.csv(x = df_expt1, 
          "3_final-processed/soc-xsit-expt1-finalData.csv",
          row.names = F)
```

## Experiment 2

### Data cleaning

```{r exp2 fix face index 6-referent condition}
# create a function to recode the face index variable in the 4-referent condition  to match the chosen index variable 
# we do this so we can know if participants selected the gaze target
convert_idx_e2 <- function(idx, numPic) {
  string_idx <- as.character(idx)
  new_idx <- switch(string_idx,
                    "-1" = -1,
                    "0" = 2,
                    "1" = 0,
                    "2" = 3,
                    "3" = 1,
                    stop("Invalid entry to switch"))
new_idx <- as.integer(new_idx)
}

# now we apply this function to each row of the data frame using rowwise()
df_expt2 %<>% 
  dplyr::rowwise() %>% 
  mutate(final_faceIdx = convert_idx_e2(idx = faceIdx, numPic = numPicN)) %>% 
  ungroup() 
```

#### Flag trials with extremely slow or fast RTs (+/- 2SD).

```{r expt2 clean RTs}
df_expt2 %<>%
  filter(rt > 0) %>% 
  mutate(include_good_rt = ifelse(log(rt) > mean(log(rt)) + 2 * sd(log(rt)) |
                                    log(rt) < mean(log(rt)) - 2 * sd(log(rt)),
                                  "exclude", "include"))
```

#### Flag social vs. no-social trials

```{r expt2 flag trial type}
df_expt2 %<>%
  mutate(condition_trial = ifelse(condition == "No-socialFirst" 
                                  & itemNum <= 7, "no-social", 
                                  ifelse(condition == "SocialFirst" 
                                         & itemNum <= 7, "social", 
                                         ifelse(condition == "No-socialFirst" 
                                                & itemNum >= 8, "social",
                                                ifelse(condition == "SocialFirst" 
                                                       & itemNum >= 8, 
                                                       "no-social", NA)))))
```

#### Flag correct exposure/test trials

```{r exp2 flag correct trials}
df_expt2 %<>%
  mutate(correct = ifelse(trial_category == "test" & chosen == kept, TRUE,
                          ifelse(trial_category == "exposure" & 
                                   condition_trial == "no-social", NA,
                                 ifelse(chosenIdx == final_faceIdx, TRUE,
                                        FALSE))))
```

#### Flag subs who got < 25% of exposure trials correct. 

```{r expt2 flag subs <25% correct on exposure}
ss_exposure <- df_expt2 %>%
  filter(trial_category == "exposure" & condition_trial == "social") %>%
  group_by(subid) %>%
  summarise(mean_acc_exp = mean(correct))

# Merge mean acc with the rest of the dataset.
df_expt2 %<>% left_join(y = ss_exposure, by = "subid")
```

#### Flag test trials on which subject chose target of gaze on exposure 

```{r expt2 flag test trials chose gaze target}
df_expt2 %<>%
  filter(trial_category == "exposure") %>%
  mutate(correct_exposure = correct,
         rt_exposure = rt) %>%
  select(subid, itemNum, correct_exposure, rt_exposure) %>%
  left_join(x = df_expt2, y = ., by = c("subid", "itemNum"))
```

#### Save clean Expt. 2 dataset

```{r save final dataset expt2}
write.csv(x = df_expt2, 
          "3_final-processed/soc-xsit-expt2-finalData.csv",
          row.names = F)
```

## Experiment 3

### Data cleaning and variable creation.

```{r expt3 cleaning 1, warning = F}
df_expt3 %<>% mutate(rel_subj = to.n(rel_subj))
```

#### Clean up variable names

```{r expt3 cleaning 2}
df_expt3$prop_cond_clean <- revalue(df_expt3$condition,
                                    c("0%_reliable" = "0%",
                                      "25%_reliable" = "25%",
                                      "50%_reliable" = "50%",
                                      "75%_reliable" = "75%",
                                      "100%_reliable" = "100%"))

# change order of condition factor for plotting
df_expt3$prop_cond_clean <- factor(df_expt3$prop_cond_clean,
                                   levels = c("0%", "25%", "50%", "75%", "100%"))

# Create continuous variable for reliability
df_expt3$reliability[df_expt3$prop_cond_clean=="0%"] <- .00
df_expt3$reliability[df_expt3$prop_cond_clean=="25%"] <- .25
df_expt3$reliability[df_expt3$prop_cond_clean=="50%"] <- .50
df_expt3$reliability[df_expt3$prop_cond_clean=="75%"] <- .75
df_expt3$reliability[df_expt3$prop_cond_clean=="100%"] <- 1.00
```

#### Clean up RTs

```{r expt3 clean RTs}
df_expt3 <- df_expt3 %>%
  filter(rt > 0) %>% 
  mutate(include_good_rt = ifelse(log(rt) > mean(log(rt)) + 2 * sd(log(rt)) | 
                                    log(rt) < mean(log(rt)) - 2 * sd(log(rt)),
                                  "exclude", "include"))
```

#### Flag whether participant chose the target of eye gaze on exposure trials in test block

```{r expt3 chose gaze target on exposure trials test block}
df_expt3 %<>% 
  filter(trial_category == "exposure", block == "test") %>% 
  select(subid, 
         gaze_target_exposure = gaze_target, 
         chosen_exposure = chosen, 
         correct_exposure = correct, 
         itemNum,
         experiment) %>% 
  left_join(x = df_expt3, by = c("subid", "itemNum", "experiment"))
```

#### Get total number of correct for each sub on exposure trials in test block

```{r}
df_expt3 %<>%
  filter(trial_category == "exposure",
         block == "test", include_good_rt == "include") %>% 
  group_by(subid, experiment) %>% 
  summarise(total_exposure_correct = sum(correct_exposure))  %>% 
  left_join(x = df_expt3, by = c("subid", "experiment"))
```

#### Get mean accuracy on each trial type for each sub

```{r}
df_expt3 %<>%
  filter(trial_category == "test",
         block == "test", include_good_rt == "include") %>% 
  group_by(subid, experiment, trialType) %>% 
  summarise(sub_mean_accuracy = mean(correct))  %>% 
  spread(key = trialType, value = sub_mean_accuracy) %>% 
  rename(same_accuracy = Same, switch_accuracy = Switch) %>% 
  left_join(x = df_expt3, by = c("subid", "experiment"))
```

#### Save clean Expt. 3 dataset 

```{r}
write.csv(x = df_expt3, 
          "3_final-processed/soc-xsit-expt3-finalData.csv",
          row.names = F)
```

## Experiment 4

### Data cleaning

#### Create variable to track experiment block.

```{r expt4 block variable}
df_expt4 %<>% mutate(block = ifelse(itemNum <= 7, "first","second"))
```

#### Flag trials with extremely slow or fast RTs (+/- 2SD).

```{r expt4 clean RTs}
df_expt4 %<>%
  filter(rt > 0) %>% 
  mutate(include_good_rt = ifelse(log(rt) > mean(log(rt)) + 2 * sd(log(rt)) |
                                    log(rt) < mean(log(rt)) - 2 * sd(log(rt)),
                                  "exclude", "include"))
```

#### Flag subs who got < 25% of exposure trials correct. 

```{r expt4 flag subs <25% correct on exposure}
ss_exposure <- df_expt4 %>%
  filter(trial_category == "exposure" & gaze_trial == "Gaze") %>%
  group_by(subid) %>%
  summarise(mean_acc_exp = mean(correct))

# Merge mean acc with the rest of the dataset.
df_expt4 %<>% left_join(y = ss_exposure, by = "subid")
```

#### Flag test trials on which subject chose target of gaze on exposure and flag if subject made a response on exposure (vs. running out of time) 

```{r expt4 flag test trials chose gaze target}
df_expt4 %<>%
  filter(trial_category == "exposure") %>%
  mutate(correct_exposure = correct, rt_exposure = rt,
         answer_type_exposure = answer_type) %>%
  select(subid, itemNum, correct_exposure, rt_exposure, answer_type_exposure) %>%
  left_join(x = df_expt4, y = ., by = c("subid", "itemNum"))
```

#### Save clean Expt. 4 dataset

```{r save final dataset expt4}
write.csv(x = df_expt4, 
          "3_final-processed/soc-xsit-expt4-finalData.csv",
          row.names = F)
```
