---
title: "Soc-xsit-live"
author: "Kyle MacDonald"
date: "December 7, 2014"
output: html_document
---

#### Analysis code for SOC-XSIT-LIVE experiment. 

Clear workspace and set working directory.

```{r clear workspace}
rm(list=ls())
setwd("/Users/kmacdonald/Documents/Projects/SOC-XSIT/SOC_XSIT/data/processed_data/adult-live")
```

Load libraries.

```{r load libraries, message=FALSE, warning=FALSE}
source("/Users/kmacdonald/Documents/programming/rscripts/useful.R")
library(reshape2)
library(plyr)
library(dplyr)
library(bootstrap)
library(lme4)
library(ggplot2)
library(RColorBrewer)
```

Read in the tidy data files for the zero delay and the three delay experiments

```{r read in data}


# read in data
df_live <- read.csv("soc_xsit_live_all.csv")

## reorder factor levels 
df_live$interval <- relevel(df_live$interval, ref = "Zero")
```

#### Get the number of subjects in each experiment and condition.

```{r get number of subs, echo=FALSE}
df_live %>%
      summarise(n_subs = n_distinct(subids))
```

#### Filters and exclusionary criteria

Flag trials with extremely slow or fast RTs (+/- 2SD).

```{r all data clean RTs}
df_live <- df_live %>%
    mutate(include_good_rt = ifelse(log(rt) > mean(log(rt)) + 2 * sd(log(rt)) |
                                        log(rt) < mean(log(rt)) - 2 * sd(log(rt)),
                                    0,1))
```

### Flag social vs. no-social trials

When we switched to within subjects, we tracked which block came first, but didn't 
track social vs. no-social. So we create a column to track this information

```{r flag social_trial_type within subs}
df_live <- df_live %>%
      mutate(condition_trial = ifelse(condition == "No-socialFirst" 
                                      & itemNum <= 7, "no-social", 
                                      ifelse(condition == "SocialFirst" 
                                             & itemNum <= 7, "social", 
                                             ifelse(condition == "No-socialFirst" 
                                                    & itemNum >= 8, "social",
                                                    ifelse(condition == "SocialFirst" 
                                                           & itemNum >= 8, 
                                                           "no-social", NA)))))
```

Flag subs who got <25% of exposure trials correct. This can be used for exclusionary criteria in later analyses. 

```{r within subs flag subs <25% correct on exposure}
# get mean acc on exposure trials for each subject
ss_exposure <- df_live %>%
      filter(trial_cat == "exposure" & condition_trial == "social") %>%
      group_by(subids) %>%
      summarise(mean_acc_exp = mean(correct))

# merge mean acc with the rest of the dataset
df_live <- merge(df_live, ss_exposure, by = "subids")
```

Flag test trials where subject chose target of eye gaze.

```{r chose target of eye gaze?}
df_test <- df_live %>%
      filter(trial_cat == "test")

# flag blocks first half vs. second half
df_test <- df_test %>%
    mutate(block = ifelse(itemNum <= 7, "first","second"))

# extract exposure trials and create a correct on exposure column 
df_expo <- df_live %>%
      filter(trial_cat == "exposure") %>%
      mutate(correct_exposure = faceIdx == chosenIdx,
             rt_exposure = rt) %>%
      select(subids, itemNum, correct_exposure, rt_exposure)

# join with test trials
df_test <- merge(df_test, df_expo)
df_test <- arrange(df_test, subids, itemNum)
```

Set up filters 

```{r within-subs filters}
# just RT filter
df_exposure <- filter(df_live,
                      include_good_rt == 1,
                      condition_trial == "social",
                      trial_cat == "exposure")

# RT, subject level and trial level filter 
df_exposure_filt <- filter(df_live,
                           trial_cat == "exposure",
                           condition_trial == "social" & mean_acc_exp > 0.25,
                           include_good_rt == 1)
```

Get the number of subjects filtered out

```{r within subs filter subjects}
#get number of subjects filtered out
df_n <- df_exposure %>%
                  summarise(n_subs = n_distinct(subids))

df_n_filt <- df_exposure_filt %>%
                        summarise(n_subs_filt = n_distinct(subids)) %>%
                        select(n_subs_filt)

cbind(df_n, df_n_filt)
```

### Accuracy on exposure trials

```{r within subs acc exposure, fig.width=10, fig.height=6}
ms_expo <- df_exposure %>%
      group_by(interval) %>%
      summarise(accuracy_exposure = mean(correct),
                ci_low = ci.low(correct),
                ci_high = ci.high(correct))

ms_expo$condition <- factor(ms_expo$condition)

acc_exp <- ggplot(data=ms_expo, 
                  aes(x=interval, y=accuracy_exposure)) + 
    geom_bar(stat="identity", fill = I("grey50")) +      
    geom_pointrange(aes(ymin=accuracy_exposure-ci_low, 
                        ymax=accuracy_exposure+ci_high), width = .1) +
    geom_hline(yintercept=0.25, linetype = "dashed") +
    scale_y_continuous(limits=c(0,1)) +
    ggtitle("Proportion chose target of eye gaze (Real)")

acc_exp
```

Now we do the same thing, but filtering out the subjects who performed below chance levels selecting the target of eye gaze. 

```{r accuracy exposure filtered}
ms_expo_filt <- df_exposure_filt %>%
      group_by(intervalNum) %>%
      summarise(accuracy_exposure = mean(correct),
                ci_low = ci.low(correct),
                ci_high = ci.high(correct))

ms_expo_filt$condition <- factor(ms_expo_filt$condition)

acc_exp_filt <- ggplot(data=ms_expo_filt, 
                       aes(x=intervalNum, y=accuracy_exposure)) + 
    geom_bar(stat="identity", fill = "dodgerblue", width=0.5) +      
    geom_linerange(aes(ymin=accuracy_exposure-ci_low, 
                        ymax=accuracy_exposure+ci_high), width = .3, size=0.8) +
    geom_hline(yintercept=0.25, linetype = "dashed") +
    scale_y_continuous(limits=c(0,1)) +
    xlab("Intervening Trials") +
    ylab("Prop. Choosing Target of Eye Gaze") +
    theme(text = element_text(size=16))   

acc_exp_filt
```

Anayze RT on exposure trials.

```{r RT exposure trials}
# delay expt
df_exposure_filt_all <- filter(df_live,
                               trial_cat == "exposure",
                               mean_acc_exp > 0.25,
                               include_good_rt == 1)

ms_rt_expo_filt <- df_exposure_filt_all %>%
    group_by(condition_trial, interval) %>%
    summarise(rt_exposure = mean(rt),
              ci_low = ci.low(rt),
              ci_high = ci.high(rt))

ms_rt_expo_filt$condition_trial <- factor(ms_rt_expo_filt$condition_trial)

ggplot(ms_rt_expo_filt, 
       aes(x=interval, y=rt_exposure, colour=condition_trial, group = condition_trial)) +
    geom_line() +
    geom_pointrange(aes(ymin=rt_exposure - ci_low,
                        ymax=rt_exposure + ci_high), width = .1, size=.7) + 
    scale_y_continuous(limits=c(1000,4000)) +
    scale_colour_manual(values=c("firebrick1", "dodgerblue"), 
                        name="Experimental\nCondition") +
    ylab("Response Time (ms)") +
    xlab("Interval between exposure and test") +
    theme(text = element_text(size=20))
```

Model RT data

```{r model rt}
df_exposure_filt_all$condition_trial <- as.factor(df_exposure_filt_all$condition_trial)

m1.rt <- lmer(rt ~ condition_trial * log2(intervalNum + 1) + (1|subids), 
               data=df_exposure_filt_all)

summary(m1.rt)
```

Explore individual subject data

```{r explore individual data exposure}
mss_expo <- df_exposure %>%
      group_by(condition, interval, condition_trial, subids) %>%
      summarise(accuracy_exposure = mean(correct))

hist_expo_live <- qplot(accuracy_exposure, geom="bar", facets=interval~condition, 
                        main = c("Histogram Acc Exposure (Real)"), data=mss_expo)

hist_expo_live
```

Explore subjects performance over trials.

```{r explore ind subs data}
dss <- df_exposure %>%
    group_by(condition, condition_trial, itemNum, interval) %>%
summarise(accuracy_exposure = mean(correct), 
              ci_low = ci.low(correct),
              ci_high = ci.high(correct))

qplot(itemNum, accuracy_exposure, col=condition, facets=interval~condition,
      geom=c("point","line"),
      data=dss) +
    scale_y_continuous(limits=c(0,1)) +
    geom_pointrange(aes(ymin=accuracy_exposure - ci_low,
                        ymax=accuracy_exposure + ci_high), width = .1)
```

#### Accuracy on test trials within subjects experiment 

Test accuracy computations with different filters. First, set up filters

```{r set up test trial filters}
# just RT filter
df_test <- filter(df_test,
                      trial_cat == "test",
                      include_good_rt == 1)

# RT, subject level and trial level filter 
df_test_filt <- filter(df_test,
                       trial_cat == "test",
                       mean_acc_exp > 0.25 ,
                       include_good_rt == 1,
                       correct_exposure == T | condition_trial == "no-social")
```

Now we do the same plots for the delay expt.

```{r acc test unfilt delay}
# No filter
ms_test <- df_test %>%
      group_by(condition, trialType, condition_trial, interval) %>%
      summarise(accuracy = mean(correct),
                ci_low = ci.low(correct),
                ci_high = ci.high(correct))

ms_test$condition <- factor(ms_test$condition)
ms_test$condition_trial <- factor(ms_test$condition_trial, 
                                  levels = c("social", "no-social"))

# means by blocks
ms_test_blocks <- df_test %>%
      group_by(block, trialType, condition_trial, interval) %>%
      summarise(accuracy = mean(correct),
                ci_low = ci.low(correct),
                ci_high = ci.high(correct))

ms_test_blocks$condition_trial <- factor(ms_test_blocks$condition_trial, 
                                  levels = c("social", "no-social"))

acc_test_plot <- ggplot(ms_test, 
                        aes(x=interval, y=accuracy, 
                            colour=condition_trial,
                            shape=trialType)) +
    geom_point(size=2)  +
    geom_pointrange(aes(ymin=accuracy - ci_low,
                        ymax=accuracy + ci_high), width = .1) +
    geom_hline(yintercept=0.25, linetype = "dashed") +
    scale_y_continuous(limits=c(0,1)) + 
    facet_grid(.~condition) +
    ggtitle("Accuracy on Same/Switch Trials")

# now plot by block
acc_test_plot_blocks <- ggplot(ms_test_blocks, 
                        aes(x=interval, y=accuracy, 
                            colour=condition_trial,
                            shape=trialType)) +
    geom_point(size=3)  +
    geom_pointrange(aes(ymin=accuracy - ci_low,
                        ymax=accuracy + ci_high), width = .1) +
    geom_hline(yintercept=0.25, linetype = "dashed") +
    scale_y_continuous(limits=c(0,1)) + 
    facet_grid(.~block) +
    ggtitle("Accuracy on Same/Switch Trials: By Block")

# now plot filtering out subjects and trials that didn't choose target of gaze 
ms_test_filt_blocks <- df_test_filt %>%
      group_by(condition_trial, trialType, block, intervalNum) %>%
      summarise(accuracy = mean(correct),
                ci_low = ci.low(correct),
                ci_high = ci.high(correct))

ms_test_filt_blocks$condition <- factor(ms_test_filt_blocks$condition)
ms_test_filt_blocks$block <- factor(ms_test_filt_blocks$block)
ms_test_filt_blocks$condition_trial <- factor(ms_test_filt_blocks$condition_trial, 
                                  levels = c("social", "no-social"))

acc_test_plot_filt_blocks <- ggplot(ms_test_filt_blocks, 
                                    aes(x=intervalNum, y=accuracy, 
                                        colour=condition_trial)) +
    geom_line(aes(linetype = trialType)) +
    geom_pointrange(aes(ymin=accuracy - ci_low,
                        ymax=accuracy + ci_high), 
                    width = .1,
                    position = "dodge",
                    size=0.5) +
    geom_hline(yintercept=0.25, linetype = "dashed") +
    scale_x_continuous(limits=c(-0.5, 3.5), breaks=c(0,3)) +
    scale_y_continuous(limits=c(0,1)) + 
    facet_grid(.~block) +
    ggtitle("Accuracy on Same/Switch Trials \n
            Within-subs (Expt 2) Separated by block")


multiplot(acc_test_plot, acc_test_plot_filt_blocks)

```

Do the same analysis within the first block. 

```{r first block acc}
df_block1 <- filter(df_test_filt, block == "first")

df_block1 %>% 
    group_by(condition_trial, intervalNum) %>%
    summarise(n_subs = n_distinct(subids))

# divide block 1 into block1a vs. block1b
df_block1 <- df_block1 %>% mutate(within_block = ifelse(itemNum <= 3, "A", "B"))

# means by block
ms_within_b1 <- df_block1 %>%
    group_by(interval, condition_trial, within_block, trialType) %>%
    summarise(accuracy = mean(correct),
                ci_low = ci.low(correct),
                ci_high = ci.high(correct))

# now plot
acc_test_block1 <- ggplot(ms_within_b1, 
                          aes(x=interval, y=accuracy, 
                              colour=condition_trial,
                              shape=trialType)) +
    geom_pointrange(aes(ymin=accuracy - ci_low,
                        ymax=accuracy + ci_high), 
                    width = .1,
                    position = "dodge",
                    size=1) +
    geom_hline(yintercept=0.25, linetype = "dashed") +
    scale_y_continuous(limits=c(0,1)) + 
    facet_grid(.~within_block) +
    ggtitle("Accuracy on Same/Switch Trials: Within Block (Filtered data)")

acc_test_block1
```

Now do the same accuracy computation but collapse across blocks

```{r acc test collapse blocks, fig.width=10, fig.height=6}
##Subject level
ms_test_collapsed <- df_test %>%
      group_by(condition_trial, trialType, interval) %>%
      summarise(accuracy = mean(correct),
                ci_low = ci.low(correct),
                ci_high = ci.high(correct))

ms_test_collapsed$condition_trial <- factor(ms_test_collapsed$condition_trial, 
                                  levels = c("social", "no-social"))

acc_test_plot_2 <- ggplot(ms_test_collapsed, 
                        aes(x=interval, y=accuracy, colour=condition_trial)) +
      geom_point(size=3) +
      geom_line(aes(linetype = trialType)) +
      geom_pointrange(aes(ymin=accuracy - ci_low,
                          ymax=accuracy + ci_high), width = .1) +
      geom_hline(yintercept=0.25, linetype = "dashed") +
      scale_y_continuous(limits=c(0,1)) + 
      ggtitle("Accuracy on Same/Switch Trials") + 
      scale_colour_manual(values=c("firebrick1", "dodgerblue")) +
      xlab("Condition") + 
      ylab("Proportion Correct") +
      labs(colour = "Trial Type") 

# Filtered 
ms_test_filt_collapsed <- df_test_filt %>%
      group_by(condition_trial, trialType, intervalNum) %>%
      summarise(accuracy = mean(correct),
                ci_low = ci.low(correct),
                ci_high = ci.high(correct))

ms_test_filt_collapsed$condition_trial <- factor(ms_test_filt_collapsed$condition_trial, 
                                  levels = c("social", "no-social"))

acc_test_filt_plot_2 <- ggplot(ms_test_filt_collapsed, 
                               aes(x=intervalNum, y=accuracy, colour = condition_trial)) +
    geom_line(aes(linetype = trialType)) +
    geom_pointrange(aes(ymin=accuracy - ci_low,
                        ymax=accuracy + ci_high), width=.1) +
    geom_hline(yintercept=0.25, linetype = "dashed") +
    scale_x_continuous(limits=c(-0.5, 3.5), breaks=c(0,3)) +
    scale_y_continuous(limits=c(0,1)) +
    scale_colour_manual(values=c("dodgerblue", "firebrick1")) +
    xlab("Intervening Trials") + 
    ylab("Prop. Choosing Repeated Referent") +
    labs(colour = "Condition", linetype = "Trial Type") +
    theme(text = element_text(size=16))

multiplot(acc_test_plot_2, acc_test_filt_plot_2, cols = 2)
```

Accuracy plot for cogsci paper

```{r acc plot cogsci}
ms_test_filt_collapsed$condition_trial<- factor(ms_test_filt_collapsed$condition_trial, 
                                           labels=c("Social", "No-social"))

ms_test_filt_collapsed$intervalFact <- as.factor(ms_test_filt_collapsed$intervalNum)

ggplot(ms_test_filt_collapsed, 
       aes(x=intervalNum, y=accuracy, colour = condition_trial)) +
    geom_line(aes(linetype = trialType), size=0.5) +
    geom_pointrange(aes(ymin=accuracy - ci_low,
                        ymax=accuracy + ci_high), 
                    width = .05, size=0.7) +
    geom_hline(yintercept=0.25, linetype = "dashed") +
    scale_x_continuous(limits=c(-.9,5), breaks=c(0, 3))+
    scale_y_continuous(limits=c(0,1)) +
    scale_colour_manual(values=c("red", "#1f78b4")) +
    xlab("Intervening Trials") + 
    ylab("Prop. Choosing Repeated Referent") +
    labs(colour = "Condition") +
    labs(linetype = "Trial Type") +
    guides(linetype=FALSE) +
    theme(text = element_text(size=16), 
          axis.title.y=element_text(vjust=1),
          axis.title.x=element_text(vjust=-0.3),
          legend.justification=c(1,1),
          legend.position = c(1,1)) 

ggsave("acc-test-expt2.pdf",dpi=600,title="Experiments 2 Accuracy",
       width = 5.4, height = 4.1,
       path = "/Users/kmacdonald/Documents/Projects/SOC_XSIT/cogsci-2015/plots_figs")
```


Look at performance on same/switch trials over time in the task.

```{r test trials over time}
ms_test_trials <- df_test %>%
      group_by(condition, trialType, itemNum) %>%
      summarise(accuracy = mean(correct),
                ci_low = ci.low(correct),
                ci_high = ci.high(correct))

ggplot(ms_test_trials, 
       aes(x=itemNum, y=accuracy, 
           colour=condition)) +
      geom_point(size = 3) +
      geom_line(size = 0.8, aes(linetype=trialType)) +
      geom_pointrange(aes(ymin=accuracy - ci_low,
                          ymax=accuracy + ci_high), width=.1) +
      geom_hline(yintercept=0.25, linetype = "dashed") +
      scale_y_continuous(limits=c(0,1)) +
      xlab("Trial Number") + 
      ylab("Proportion Correct") +
      labs(colour = "Condition", linetype = "Trial Type") +
      theme(text = element_text(size=20))

ms_test_trials_block <- df_test %>%
      group_by(condition, trialType, block) %>%
      summarise(accuracy = mean(correct),
                ci_low = ci.low(correct),
                ci_high = ci.high(correct))

ggplot(ms_test_trials_block, 
       aes(x=condition, y=accuracy, colour=trialType, group=trialType)) +
    geom_point(size = 3) +
    geom_line() + 
    geom_pointrange(aes(ymin=accuracy - ci_low,
                    ymax=accuracy + ci_high), width=.1) +
    facet_wrap(~block) +
    geom_hline(yintercept=0.25, linetype = "dashed") +
    scale_y_continuous(limits=c(0,1)) +
    scale_colour_manual(values=c("firebrick1", "dodgerblue")) +
    xlab("Block") + 
    ylab("Proportion Correct") +
    labs(colour = "Trial Type") +
    theme(text = element_text(size=20))

```

RT on test trials

```{r RT test trials}
ms_test_filt_rt <- df_test_filt %>%
      group_by(condition_trial, trialType) %>%
      summarise(rt_test = mean(rt),
                ci_low = ci.low(rt),
                ci_high = ci.high(rt))

ms_test_filt_rt$condition_trial <- factor(ms_test_filt_rt$condition_trial, 
                                  levels = c("social", "no-social"))

rt_test_filt_plot <- ggplot(ms_test_filt_rt, 
                             aes(x=condition_trial, y=rt_test, 
                                 group=trialType, colour=trialType)) +
      geom_point(size = 3) +
      geom_line(size = 0.8) +
      geom_pointrange(aes(ymin=rt_test - ci_low,
                          ymax=rt_test + ci_high), width=.1) + 
      scale_colour_manual(values=c("firebrick1", "dodgerblue")) +
      xlab("Condition") + 
      ylab("Response Time") +
      labs(colour = "Trial Type") +
      theme(text = element_text(size=20))

```

##### Model the data

```{r model data}
# subject level and trial level filter
m1_live <- glmer(correct ~ trialType * condition_trial * intervalNum + 
                       (trialType | subids), nAGQ=0,
            data = df_test_filt,
            family=binomial)
summary(m1_live)
```

Model accuracy on test trials using RT as predictor. First RT on test trials:

```{r model using RT as predictor}
m2_live <- glmer(correct ~ trialType * condition_trial * intervalNum * rt + 
                       (trialType | subids), nAGQ=0,
            data = df_test_filt,
            family=binomial)
summary(m2_live)
```

Now model using RT on learning trials

```{r model using RT as predictor}
m3_live <- glmer(correct ~ trialType * condition_trial * intervalNum * log2(rt_exposure) + 
                       (trialType | subids), nAGQ=0,
            data = df_test_filt,
            family=binomial)
summary(m3_live)
```

#### Stats

Get the null distribution expected under a binomial guessing model
```{r nulls}
# null model
null <- dbinom(c(0,1,2,3,4), 4, 0.25)
```

Get the total number correct for each subject by trial type, condition, and number of referents

```{r binom}
mss <- df_test_filt %>%
    group_by(subids, trialType, intervalNum, condition_trial) %>%
    summarise(count_correct = sum(correct), 
              n = 4)

ss <- mss %>%
    group_by(trialType, intervalNum, condition_trial) %>%
    summarise(num_correct = sum(count_correct), 
              n = sum(n), 
              dist_correct = num_correct / n)
```

Chi-square comparing distribution of correct responses to guessing model

```{r chi square}
chisq <- chisq.test(ss$dist_correct,p=nulls[i,],simulate.p=FALSE)
```
