---
title: "Soc-Xsit Vizualizations and Models"
author: "Kyle MacDonald"
date: "January 17, 2015"
output: html_document
---

```{r global_options, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=10, fig.height=8, fig.crop = F, echo = F,
                      warning=FALSE, cache=F, message=FALSE, sanitize = T)
```

This script creates visualizations and models for our Social Cross-situational Word Learning Project.

Clear workspace and set working directory 

```{r clear workspace, echo=F, warning=F}
source("helpers/useful.R")
library(pander)
library(magrittr)
library(gridExtra)
library(tidyr)
library(directlabels)
```

Read in data from all 3 Experiments:

* Experiment 1: Large scale experiment manipulating attention and memory demands
* Experiment 2: Replication of Experiment 1 with more ecologically valid stimulus set
* Experiment 3: Parametric manipulation of cue reliablity

```{r read data, echo=F, warning=F}
df_expt1 <- read.csv("../data/final-processed/soc-xsit-expt1-finalData.csv")
df_expt2 <- read.csv("../data/final-processed/soc-xsit-expt2-finalData.csv")
df_expt3 <- read.csv("../data/final-processed/soc-xsit-expt3-finalData.csv")
```

## Experiment 1

### Get the number of subjects in each condition.  

```{r describe data, tidy=TRUE}
nsubs <- df_expt1 %>%
    group_by(condition, intervalNum, numPicN) %>%
    summarise(n_subs = n_distinct(subids))

knitr::kable(nsubs)
```

### Set up filters 

Get test trials for analysis. Here we have 2 filters:

* Remove fast/slow RTs
* Remove fast/slow RTs & subjects who performed below 
chance selecting gaze target on exposure trials

```{r expt1 test trials}
# just RT filter
df_expo_expt1 <- df_expt1 %>%  
    filter(trial_category == "exposure", include_good_rt_exposure == "include")

df_test_expt1 <- df_expt1 %>%  
    filter(trial_category == "test", include_good_rt_test == "include",
           correct_exposure == T | condition == "No-Social")

# subject and trial level filter
df_test_expt1_filt <- df_expt1 %>% 
    filter(trial_category == "test") %>% 
    filter(include_good_rt_test == "include", 
           include_expo == "include" | condition == "No-Social") %>%
    filter(correct_exposure == T | condition == "No-Social")

df_expo_expt1_analysis <- df_expt1 %>%
    filter(trial_category == "exposure") %>% 
    filter(include_good_rt_exposure == "include", 
           include_expo == "include" | condition == "No-Social") %>%
    filter(correct_exposure == T | condition == "No-Social")
```

Get the number of subjects filtered out

```{r expt1 nsubs filtered}
df_n <- df_test_expt1 %>%
    group_by(condition) %>%
    summarise(n_subs = n_distinct(subids))

df_n_filt <- df_test_expt1_filt %>%
    group_by(condition) %>%
    summarise(n_subs_filt = n_distinct(subids)) %>%
    select(n_subs_filt)

df_n <- cbind(df_n, df_n_filt)

knitr::kable(df_n)
```

### Accuracy on exposure trials in social condition

Get means and CIs for each combination of number of referents and interval

```{r expt1 accuracy on exposure trials}
ms_expo_expt1 <-  df_expo_expt1 %>%
    filter(condition == "Social") %>%
    group_by(numPic, intervalNum) %>%
    summarise(accuracy_exposure = mean(correct_exposure),
              ci_low = ci.low(correct_exposure),
              ci_high = ci.high(correct_exposure))
```

Now plot those means.

```{r expt 1 accuracy on exposure trials plot, echo=F}
ggplot(data=ms_expo_expt1, 
       aes(x=intervalNum, y=accuracy_exposure)) + 
    geom_pointrange(aes(ymin=accuracy_exposure - ci_low, 
                        ymax=accuracy_exposure + ci_high), size=0.6) +
    geom_smooth(method = "lm", se = F) +
    geom_hline(aes(yintercept=1/numPic), linetype = "dashed") +
    scale_x_continuous(limits=c(-.9,8), breaks=c(0, 1, 3, 7)) +
    scale_y_continuous(limits=c(0,1)) +
    scale_colour_manual(values=c("#1f78b4", "red")) +
    facet_grid( ~ numPic) + 
    xlab("Intervening Trials") + 
    ylab("Prop. Chose Gaze Target") +
    labs(colour = "Condition") +
    labs(linetype = "Trial Type") +
    guides(linetype=FALSE) +
    theme(text = element_text(size=14), 
          axis.title.y=element_text(vjust=1),
          axis.title.x=element_text(vjust=-0.3),
          legend.justification=c(0,0),
          legend.position = c(0,0)) 
```

### RT on exposure trials 

Next we compare reaction times across social/no-social at different 
levels of attention and memory demands.

```{r expt1 rt on exposure trials}
ms_expo_rt_expt1 <-  df_expo_expt1_analysis %>%
    group_by(numPic, intervalNum, condition) %>%
    summarise(mean_rt = mean(rt),
              ci_low = ci.low(rt),
              ci_high = ci.high(rt))
```

Now we plot mean reaction times for each condition.

```{r expt1 rt labels, echo=F}
# change factor labels 
ms_expo_rt_expt1$condition <- revalue(ms_expo_rt_expt1$condition,
                                      c("No-Social" = "No-Gaze","Social" = "Gaze"))
```

```{r expt1 plot rt on exposure trials, echo=F}
exp1_rt_exposure_plot <- ggplot(data=ms_expo_rt_expt1, 
                                aes(x=intervalNum, y=mean_rt, color = condition)) + 
    geom_linerange(aes(ymin=mean_rt - ci_low, 
                        ymax=mean_rt + ci_high), size=1) +
    geom_point(size=5) +
    scale_x_continuous(limits=c(-.9,9.5), breaks=c(0, 1, 3, 7)) +
    geom_smooth(method="lm", se =F) +
    scale_y_continuous(limits=c(0,5200)) +
   # scale_colour_grey(start = 0.3, end = 0.6) +
    scale_colour_manual(values=c("#2c7fb8", "#e34a33")) +
    facet_grid( ~ numPic) + 
    xlab("Interval Between Exposure and Test") + 
    ylab("Reponse Time (ms)") +
    labs(colour = "Condition") +
    labs(linetype = "Trial Type") +
    guides(linetype=FALSE, color=F) +
    theme(
        title = element_text(size = 24),
        axis.title.x = element_text(colour="black",size=22,
                                    angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.text.x = element_text(colour="grey20",size=18,
                                   angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.text.y = element_text(colour="grey20",size=18,
                                   angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.title.y = element_text(colour="black",size=22,face="plain"),
        legend.position=c(0.1,0.2),
        legend.text = element_text(size=18),
        legend.title = element_text(size=20, face="bold"),
        strip.text = element_text(size=16),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_line(colour = "gray88", linetype = "solid"),
        panel.margin = unit(1, "lines")
    )
```

### Accuracy on test trials 

```{r expt1 acc test}
ms_test_expt1 <- df_test_expt1  %>%
    group_by(condition, intervalNum, numPic, trialType) %>%
    summarise(accuracy = mean(correct),
              ci_low = ci.low(correct),
              ci_high = ci.high(correct),
              exclusionary_criteria = "Trial Level")

ms_test_filt_expt1 <- df_test_expt1_filt  %>%
    group_by(condition, intervalNum, numPic, trialType) %>%
    summarise(accuracy = mean(correct),
              ci_low = ci.low(correct),
              ci_high = ci.high(correct),
              exclusionary_criteria = "Subject and Trial level")

ms_test_all_expt1 <- rbind(ms_test_expt1, ms_test_filt_expt1)
```

```{r expt1 acc test plot revalue, echo=F}
ms_test_expt1$condition <- revalue(ms_test_expt1$condition,
                                   c("No-Social" = "No-Gaze","Social" = "Gaze"))
```

```{r expt1 acc test plot, echo=F}
expt1.acc.test <- ggplot(data=ms_test_expt1, 
                         aes(x=intervalNum, y=accuracy, 
                             colour = condition, lineType = trialType)) + 
    geom_point(size=5) +
    geom_smooth(method="lm", se =F) +
    geom_linerange(aes(ymin=accuracy - ci_low, 
                       ymax=accuracy + ci_high), size=1) +
    #geom_line(aes(linetype = trialType), size=0.4) +
    geom_hline(aes(yintercept=1/numPic), linetype = "dashed") +
    scale_x_continuous(limits=c(-.9,8), breaks=c(0, 1, 3, 7)) +
    scale_y_continuous(limits=c(0,1)) +
    #scale_colour_grey(start = 0.3, end = 0.6) +
    scale_colour_manual(values=c("#2c7fb8", "#e34a33")) +
    facet_grid(. ~ numPic) + 
    xlab("Interval Between Exposure and Test") + 
    ylab("Proportion Correct") +
    labs(colour = "Condition") +
    labs(linetype = "Trial Type") +
    guides(linetype=FALSE) +
    theme(
        axis.title.x = element_text(colour="black",size=22,
                                    angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.text.x = element_text(colour="grey20",size=18,
                                   angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.text.y = element_text(colour="grey20",size=18,
                                   angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.title.y = element_text(colour="black",size=22,face="plain"),
        legend.position=c(0.08,0.2),
        legend.text = element_text(size=18),
        legend.title = element_text(size=20, face="bold"),
        strip.text = element_text(size=16),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_line(colour = "gray88", linetype = "solid"),
        panel.margin = unit(1, "lines")
    )
```

```{r}
grid.arrange(exp1_rt_exposure_plot, expt1.acc.test, ncol=1)
```

### LMERs

#### Predicting RT on exposure trials.

```{r expt1 lmer rt}
m1_rt_expt1 <- lmer(rt_exposure ~ condition * log2(intervalNum + 1) * log2(numPicN) + 
                        (1|subids), data=df_expo_expt1_analysis)

knitr::kable(summary(m1_rt_expt1)$coef, digits = 3)
```

#### Predict accuracy on test trials.

```{r expt1 lmer acc test}
# 2-way model
m1_2way_expt1 <- glmer(correct ~ (trialType + condition + log2(intervalNum + 1) + log2(numPicN))^2 + 
                           (trialType | subids), 
                       data=df_test_expt1_filt, 
                       family=binomial, 
                       nAGQ=0)

# 3-way model
m1_3way_expt1 <- glmer(correct ~ (trialType + condition + log2(intervalNum + 1) + log2(numPicN))^3 + 
                           (trialType | subids), 
                       data=df_test_expt1_filt, 
                       family=binomial, 
                       nAGQ=0)

# 4-way model
m1_4way_expt1 <- glmer(correct ~ (trialType + condition + log2(intervalNum + 1) + log2(numPicN))^4 + 
                           (trialType | subids), 
                       data=df_test_expt1_filt, 
                       family=binomial, 
                       nAGQ=0)

# model comparison
model_comp <- anova(m1_2way_expt1, m1_3way_expt1, m1_4way_expt1)

knitr::kable(model_comp)
```

3-way model is best based on model comparison, but not theoretically motivated. So we stick with the 
2-way interactions model as the key test of our hypothesis. 

## Experiment 2

In Experiment 2, we chose a subset of the referent/interval conditions: 
numPic = 4, and interval = 0 and 3.

Get the number of subjects in each condition.

```{r expt2 nsubs}
nsubs_expt2 <- df_expt2 %>% 
    group_by(condition, interval) %>%
    summarise(n_subs = n_distinct(subids))

knitr::kable(nsubs_expt2)
```

### Set up filters

Exposure trials.

```{r expt2 expo filters}
# just RT filter
df_expo_expt2 <- filter(df_expt2,
                        include_good_rt == "include",
                        condition_trial == "social",
                        trial_cat == "exposure")

# RT, subject level and trial level filter 
df_expo_expt2_filt <- filter(df_expt2,
                             trial_cat == "exposure",
                             condition_trial == "social" & mean_acc_exp > 0.25,
                             include_good_rt == "include")

# filter that gets both social/no-social trials
df_expo_expt2_analysis <- df_expt2 %>%
    filter(trial_cat == "exposure",
           mean_acc_exp > 0.25,
           correct_exposure = T | condition_trial == "no-social",
           include_good_rt == "include")
```

Get the number of subjects filtered out by the subject level filter.

```{r expt2 nsubs filtered}
df_n_expt2 <- df_expo_expt2 %>%
    group_by(condition) %>%
    summarise(n_subs = n_distinct(subids))

df_n_expt2_filt <- df_expo_expt2_filt %>%
    group_by(condition) %>%
    summarise(n_subs_filt = n_distinct(subids)) %>%
    select(n_subs_filt)

nsubs_expt2_filt <- cbind(df_n_expt2, df_n_expt2_filt)

knitr::kable(nsubs_expt2_filt)
```

Test trial filters.

```{r expt2 test filters}
# just RT filter
df_test_expt2 <- df_expt2 %>%
    filter(trial_cat == "test",
           include_good_rt == "include")

# RT, subject level and trial level filter 
df_test_expt2_filt <- df_expt2 %>%
    filter(trial_cat == "test",
           mean_acc_exp > 0.25 ,
           include_good_rt == "include",
           correct_exposure == T | condition_trial == "no-social")
```

### Analyze Exposure Trials

Accuracy, selecting target of gaze.

```{r expt2 acc expo}
# unfiltered
ms_expo_expt2 <- df_expo_expt2 %>%
    group_by(intervalNum) %>%
    summarise(accuracy_exposure = mean(correct),
              ci_low = ci.low(correct),
              ci_high = ci.high(correct)) %>%
    mutate(filter = "Unfiltered")

# filtered
ms_expo_expt2_filt <- df_expo_expt2_filt %>%
    group_by(intervalNum) %>%
    summarise(accuracy_exposure = mean(correct),
              ci_low = ci.low(correct),
              ci_high = ci.high(correct)) %>%
    mutate(filter = "Filtered")

ms_expo_all_expt2 <- rbind(ms_expo_expt2, ms_expo_expt2_filt)
```

Now plot mean correct for exposure trials for each interval.

```{r expt2 acc expo plot, echo=F}
ggplot(data=ms_expo_all_expt2, 
       aes(x=intervalNum, y=accuracy_exposure)) + 
    geom_pointrange(aes(ymin=accuracy_exposure - ci_low, 
                        ymax=accuracy_exposure + ci_high), size=0.6) +
    geom_hline(aes(yintercept=1/4), linetype = "dashed") +
    scale_x_continuous(limits=c(-.9,4), breaks=c(0,3)) +
    scale_y_continuous(limits=c(0,1)) +
    scale_colour_manual(values=c("#1f78b4", "red")) +
    xlab("Intervening Trials") + 
    ylab("Prop. Choosing Repeated Referent") +
    labs(colour = "Condition") +
    labs(linetype = "Trial Type") +
    guides(linetype=FALSE) +
    facet_grid(~filter) +
    theme(text = element_text(size=14), 
          axis.title.y=element_text(vjust=1),
          axis.title.x=element_text(vjust=-0.3),
          legend.justification=c(0,0),
          legend.position = c(0,0)) 
```

RT on exposure trials.

```{r expt2 rt expo}
ms_rt_expo_expt2 <- df_expo_expt2_analysis %>%
    group_by(condition_trial, intervalNum) %>%
    summarise(rt_exposure = mean(rt),
              ci_low = ci.low(rt),
              ci_high = ci.high(rt))
```

Plot RT differences

```{r expt2 rt expo plot, echo=F}
# revalue social/no-social --> gaze/no-gaze
ms_rt_expo_expt2$condition <- revalue(ms_rt_expo_expt2$condition,
                                      c("no-social" = "No-Gaze", "social" = "Gaze"))

expt2.rt.expo <- ggplot(data=ms_rt_expo_expt2, 
                        aes(x=intervalNum, y=rt_exposure, color = condition)) + 
    geom_pointrange(aes(ymin=rt_exposure - ci_low, 
                        ymax=rt_exposure + ci_high), size=1.5) +
    scale_x_continuous(limits=c(-.9,4), breaks=c(0,3)) +
    geom_smooth(method="lm", se=F) +
    scale_y_continuous(limits=c(0,5000)) +
    scale_colour_manual(values=c("#e34a33", "#2c7fb8")) +
    #scale_color_grey(start = 0.3, end = 0.6) + 
    xlab("Intervening Trials") + 
    ylab("Response Time (ms)") +
    labs(colour = "Condition") +
    labs(linetype = "Trial Type") +
    ggtitle("Study Time on Exposure Trials") + 
    #guides(linetype=FALSE, color=F) +
    theme(axis.title.x = element_text(colour="black",size=22,
                                      angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.text.x = element_text(colour="grey20",size=18,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.text.y = element_text(colour="grey20",size=18,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.title.y = element_text(colour="black",size=22,face="plain"),
          #legend.position=c(0.82,0.80),
          legend.text = element_text(size=20),
          legend.title = element_text(size=22, face="bold"),
          plot.title = element_text(lineheight=1, face="bold", size = 24),
          strip.text = element_text(size=16))
```

## Analyze test trials

Get means and CIs for each condition.

```{r expt2 acc test aggregate}
# unfiltered
ms_test_expt2 <- df_test_expt2 %>%
    group_by(trialType, condition_trial, intervalNum) %>%
    summarise(accuracy = mean(correct),
              ci_low = ci.low(correct),
              ci_high = ci.high(correct)) %>%
    mutate(filter = "Unfiltered")

# filtered (subject level)
ms_test_expt2_filt <- df_test_expt2_filt %>%
    group_by(trialType, condition_trial, intervalNum) %>%
    summarise(accuracy = mean(correct),
              ci_low = ci.low(correct),
              ci_high = ci.high(correct)) %>%
    mutate(filter = "Filtered")

ms_test_all_expt2 <- rbind(ms_test_expt2, ms_test_expt2_filt)
```

Now plot accuracy for test trials.

```{r expt2 acc test plot, echo=F}
# revalue social/no-social --> gaze/no-gaze
ms_test_expt2_filt$condition_trial <- revalue(ms_test_expt2_filt$condition_trial,
                                              c("no-social" = "No-Gaze", "social" = "Gaze"))

expt2.acc.test <- ggplot(data=ms_test_expt2_filt, 
                         aes(x=intervalNum, y=accuracy, 
                             colour = condition_trial)) + 
    geom_line(aes(linetype = trialType), size=0.6) +
    geom_pointrange(aes(ymin=accuracy - ci_low, 
                        ymax=accuracy + ci_high), size=1.5) +
    geom_hline(aes(yintercept=1/4), linetype = "dashed") +
    scale_x_continuous(limits=c(-.9,4), breaks=c(0, 3)) +
    scale_y_continuous(limits=c(0,1)) +
    scale_colour_manual(values=c("#e34a33", "#2c7fb8")) +
    #scale_colour_grey(start=0.6, end=0.3) +
    xlab("Intervening Trials") + 
    ylab("Proportion Correct") +
    labs(colour = "Condition") +
    labs(linetype = "Trial Type") +
    guides(linetype=FALSE) +
    ggtitle("Accuracy on Test Trials") +
    theme(axis.title.x = element_text(colour="black",size=22,
                                      angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.text.x = element_text(colour="grey20",size=18,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.text.y = element_text(colour="grey20",size=18,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.title.y = element_text(colour="black",size=22,face="plain"),
          #legend.position=c(0.80,0.88),
          legend.text = element_text(size=20),
          legend.title = element_text(size=22, face="bold"),
          plot.title = element_text(lineheight=1, face="bold", size = 24),
          strip.text = element_text(size=16))
```

```{r expt2_paper_plot}
grid.arrange(expt2.rt.expo, expt2.acc.test, ncol=2)
```

### LMERs 

Predicting RT on exposure trials.

```{r expt2 lmer rt}
m1_rt_expt2 <- lmer(rt ~ condition_trial * log2(intervalNum + 1) + (1|subids), 
                    data=df_expo_expt2_analysis)

knitr::kable(summary(m1_rt_expt2)$coef, digits = 3)
```

Comparing models with different levels of complexity.

```{r expt 2 lmers model comparison}
# filtered 2-way
m1_expt2_2way_filt <- glmer(correct ~ (trialType + condition_trial + intervalNum)^2 + 
                                (trialType | subids), nAGQ=0,
                            data = df_test_expt2_filt,
                            family=binomial)

# filtered 3-way
m1_expt2_3_way_filt <- glmer(correct ~ (trialType + condition_trial + intervalNum)^3 + 
                                 (trialType | subids), nAGQ=0,
                             data = df_test_expt2_filt,
                             family=binomial)

model_comp_expt2 <- anova(m1_expt2_2way_filt, m1_expt2_3_way_filt)

knitr::kable(model_comp_expt2)
```

3-way is no better than the 2-way.

### LMER Test Trials

```{r expt2 lmers filters}
# filtered 2-way
m1_expt2_filt <- glmer(correct ~ (trialType + condition_trial + intervalNum)^2 + 
                           (trialType | subids), nAGQ=0,
                       data = df_test_expt2_filt,
                       family=binomial)

knitr::kable(summary(m1_expt2_filt)$coef, digits = 3)
```

Model output is no different when we use the filtered data.

## Experiment 3

### Get the number of subjects in each experiment and condition.

```{r expt3 get number of subs}
n_subs_expt3 <- df_expt3 %>%
    group_by(prop_cond_clean, experiment) %>%
    summarise(n_subs = n_distinct(subids))

knitr::kable(n_subs_expt3)
```

Fix factor order for reliablity conditions

```{r, echo = F}
df_expt3$prop_cond_clean <- factor(df_expt3$prop_cond_clean,
                                   levels = c("0%", "25%", "50%", "75%", "100%"))
```

#### Analyze Familiarization Block

RT on exposure trials.

```{r expt3 rt exposure trials fam block}
ms_rt_expo_fam <- df_expt3 %>%
    filter(trial_category == "exposure", block == "familiarization", 
           include_good_rt == "include", experiment == "replication") %>% 
    group_by(prop_cond_clean, experiment) %>%
    summarise(rt_exposure = mean(rt),
              ci_low = ci.low(rt),
              ci_high = ci.high(rt))
```

```{r expt 3 rt exposure trials plot}
ggplot(ms_rt_expo_fam, 
       aes(x=prop_cond_clean, y=rt_exposure)) +
    geom_pointrange(aes(ymin=rt_exposure - ci_low,
                        ymax=rt_exposure + ci_high), size = 0.8) + 
    scale_y_continuous(limits=c(500,4500)) +
    ylab("Response Time (ms)") +
    xlab("Level of Reliability") +
    theme(text = element_text(size=16),
          axis.text.x  = element_text(angle=0, vjust=0.5, size=12))
```

Accuracy on test trials in familiarization block

```{r expt3 acc test trials familiarization block}
ms_test_fam <- df_expt3 %>%
    filter(trial_category == "test", block == "familiarization", 
           include_good_rt == "include", experiment == "replication") %>% 
    group_by(prop_cond_clean, trialType) %>%
    summarise(accuracy = mean(correct),
              ci_low = ci.low(correct),
              ci_high = ci.high(correct))
```

```{r, echo = F}
ggplot(ms_test_fam, 
       aes(x=prop_cond_clean, y=accuracy, 
           group=trialType, colour=trialType)) +
    geom_pointrange(aes(ymin=accuracy - ci_low,
                        ymax=accuracy + ci_high), size=0.7) +
    geom_hline(yintercept=0.5, linetype = "dashed") +
    scale_y_continuous(limits=c(0,1)) + 
    geom_smooth(method='lm') +
    ggtitle("Accuracy on Test Trials in Familiarization Block")
```

Split this by first and second half. 

```{r expt3 acc test trials familiarization block split}
ms_test_fam_blocked <- df_expt3 %>%
    filter(trial_category == "test", block == "familiarization", 
           include_good_rt == "include", experiment == "replication") %>% 
    mutate(second_half = ifelse(itemNum > 3, "First Block", "Second Block")) %>%
    group_by(prop_cond_clean, trialType, second_half) %>%
    summarise(accuracy = mean(correct),
              ci_low = ci.low(correct),
              ci_high = ci.high(correct))
```

Plot. 

```{r, echo = F}
ggplot(ms_test_fam_blocked, 
       aes(x=prop_cond_clean, y=accuracy, 
           group=trialType, colour=trialType)) +
    geom_pointrange(aes(ymin=accuracy - ci_low,
                        ymax=accuracy + ci_high), size=0.7) +
    geom_hline(yintercept=0.5, linetype = "dashed") +
    scale_y_continuous(limits=c(0,1)) + 
    geom_smooth(method='lm') +
    facet_grid(. ~ second_half) + 
    ggtitle("Accuracy on Test Trials in Familiarization Block")
```

#### Analyze performance on test block

Anayze RT on exposure trials in the test block.

```{r expt3 rt exposure trials test block}
ms_rt_expo_test <- df_expt3 %>%
    filter(trial_category == "exposure", block == "test", 
           include_good_rt == "include", experiment == "replication") %>% 
    group_by(prop_cond_clean, trialType) %>%
    summarise(rt_exposure = mean(rt),
              ci_low = ci.low(rt),
              ci_high = ci.high(rt))
```

Plot. 

```{r rt exposure trials exposure block}
ggplot(ms_rt_expo_test, 
       aes(x=prop_cond_clean, y=rt_exposure, color = trialType)) +
    geom_pointrange(aes(ymin=rt_exposure - ci_low,
                        ymax=rt_exposure + ci_high), size = 0.8) + 
    scale_y_continuous(limits=c(500,4500)) +
    ylab("Response Time (ms)") +
    xlab("Condition") +
    theme(text = element_text(size=14))
```

Accuracy on familiarization trials in test block

```{r expt3 acc fam trials in test block}
ms_expo_test <- df_expt3 %>%
        filter(trial_category == "exposure", block == "test", 
           include_good_rt == "include", experiment == "replication") %>% 
    group_by(prop_cond_clean) %>%
    summarise(accuracy = mean(correct_exposure, na.rm=T),
              ci_low = ci.low(correct_exposure),
              ci_high = ci.high(correct_exposure),
              mean_rel = mean(rel_subj, na.rm=T),
              ci_low_rel = ci.low(rel_subj),
              ci_high_rel = ci.high(rel_subj)
              )
```

Now plot chose target of gaze

```{r chose gaze target plot}
ggplot(ms_expo_test, 
       aes(x=prop_cond_clean, y=accuracy, group=1)) +
    geom_smooth(method="lm", se=F, color="black") +
    geom_pointrange(aes(ymin=accuracy - ci_low,
                        ymax=accuracy + ci_high), size=1, color = "black") +
    geom_hline(yintercept=0.25, linetype = "dashed") +
    scale_y_continuous(limits=c(0,1)) +
    xlab("Level of Reliablity") + 
    ylab("Prop. Chose Target of Gaze") + 
    theme(axis.title.x = element_text(colour="black",size=16,
                                      angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.title.y = element_text(colour="black",size=16,
                                      angle=90,hjust=0.5,vjust=0.5,face="plain"),
          axis.text.x = element_text(colour="grey20",size=12,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.text.y = element_text(colour="grey20",size=12,
                                     angle=0,hjust=0.5,vjust=0,face="plain"))

```

Accuracy on test trials in the test block

```{r expt3 acc on test trials test block}
ms_test_test <- df_expt3 %>%
    filter(trial_category == "test", block == "test", 
           include_good_rt == "include") %>% 
    group_by(prop_cond_clean, trialType) %>%
    summarise(accuracy = mean(correct),
              ci_low = ci.low(correct),
              ci_high = ci.high(correct))
```

Analyze subject reported reliablity

```{r subjective reliablity analysis 1}
ms_test_subj_rel <- df_expt3 %>%
    filter(experiment == "replication") %>% 
    mutate(rel_subj = as.numeric(as.character(rel_subj))) %>% 
    group_by(prop_cond_clean) %>%
    summarise(subjective_reliability = mean(rel_subj, na.rm=T),
              ci_low = ci.low(rel_subj),
              ci_high = ci.high(rel_subj))
```

Plot relationship between reliablity condition and subjective reliabiltiy judgments.

```{r}
qplot(x = prop_cond_clean, y = subjective_reliability,
      group=1, data=ms_test_subj_rel) + 
    ylim(c(0,1)) +
    geom_smooth(method="lm", se=T) +
    xlab("Reliablity Condition") +
    ylab("Subjective Reliablity Judgment")
```

Summarise subjective reliablity at the participant level.

```{r expt3 summarise subjective reliablity}
mss_subj_rel <- df_expt3 %>% 
    filter(experiment == "replication", is.na(rel_subj) == F) %>% 
    select(subids, rel_subj, prop_cond_clean, total_exposure_correct, 
           same_accuracy, switch_accuracy, experiment) %>% 
    distinct()
```

Histogram across conditions

```{r}
qplot(rel_subj, facets=.~prop_cond_clean, 
      data=mss_subj_rel, binwidth = 0.1) +
    xlab("Subjective Reliability Judgment")
```

Reported reliability vs. number correct on exposure - individual consistency.

```{r subjective reliablity analysis 2}
qplot(total_exposure_correct, rel_subj, col = prop_cond_clean, 
      data=mss_subj_rel) + geom_smooth(method="lm", se=FALSE)
```

Reported reliability vs. number correct on exposure - means.

```{r subjective reliablity analysis 3}
ms_test_subj_rel <- df_expt3 %>%
    filter(experiment == "replication", include_good_rt == "include", is.na(rel_subj) == F) %>% 
    group_by(prop_cond_clean, total_exposure_correct) %>%
    summarise(subj = mean(rel_subj, na.rm=TRUE), 
              cih = ci.high(rel_subj),
              cil = ci.low(rel_subj))
```

Plot.

```{r expt3 subj rel plot}
qplot(total_exposure_correct, subj, col = prop_cond_clean, 
      ymin = subj - cil, ymax = subj + cih,
      geom="pointrange",
      position=position_dodge(width=.1),
      data=ms_test_subj_rel, ylab="Subjective reliability", 
      xlab="Num Trials Chose Gaze Target") + 
    geom_smooth(method="lm", se=FALSE) +
    scale_color_discrete(name="Reliability Level") +
    theme(axis.title.x = element_text(colour="black",size=16,
                                      angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.title.y = element_text(colour="black",size=16,
                                      angle=90,hjust=0.5,vjust=0.5,face="plain"),
          axis.text.x = element_text(colour="grey20",size=12,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.text.y = element_text(colour="grey20",size=12,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          legend.text = element_text(size=13),
          legend.title = element_text(size=13, face="bold"))
```

Relationship between subjective reliability, reliablity condition, and test trial performance

```{r expt3 subj reliablity munging}
gather_mss_rel_subj <- mss_subj_rel %>% 
    gather(key = trialType, value = sub_mean_accuracy, 5:6) %>% 
    arrange(subids)

gather_mss_rel_subj$rel_bin <- cut(gather_mss_rel_subj$rel_subj, breaks = 5, 
                                   labels = c("0.0-0.2", "0.2-0.4", "0.4-0.6", "0.6-0.8", "0.8-1.0" )
                                   )

ms_rel_subj <- gather_mss_rel_subj %>% 
    group_by(rel_bin, trialType) %>% 
    summarise(mean_accuracy = mean(sub_mean_accuracy, na.rm = T),
              ci_low = ci.low(sub_mean_accuracy),
              ci_high = ci.high(sub_mean_accuracy))
```

```{r expt3 acc test by acc exposure plot, echo=F}
ms_acc_exp_test_expt3 <- df_expt3 %>%
    filter(trial_category == "test", block == "test",
           include_good_rt == "include", experiment == "replication") %>% 
    group_by(trialType, total_exposure_correct) %>%
    summarise(cih = ci.high(correct), 
              cil= ci.low(correct),
              correct = mean(correct))
```

## LMERs Experiment 3

### Accuracy on exposure trials in test block.

```{r expt3 lmer acc expo test block}
m1_expo_expt3 <- glmer(correct ~ reliability + (1 | subids),
                       data = filter(df_expt3, trial_category == "exposure", block == "test",
                                     experiment == "replication", include_good_rt == "include"),
                       nAGQ = 0,
                       control = glmerControl(optimizer = "bobyqa"),
                       family = binomial)

knitr::kable(summary(m1_expo_expt3)$coef)
```

Participants are more likely to select the target of gaze when the gaze cue is more reliable.

#### Predict gaze following based on subjective reliability judgments.

```{r glm expt 3 gaze following}
m1_subj_rel_expt3 <- glmer(correct ~ rel_subj + (1 | subids),
                       data = filter(df_expt3, trial_category == "exposure", block == "test",
                                     experiment == "replication", include_good_rt == "include"),
                       nAGQ = 0,
                       control = glmerControl(optimizer = "bobyqa"),
                       family = binomial)

knitr::kable(summary(m1_subj_rel_expt3)$coef)
```

Participants who rate the cue as more reliable are also more likely to use the cue

### Accuracy on test trials in test block.

```{r expt3 glmer rel condition as continuous}
m2_expt3 <- glmer(correct ~ trialType * reliability + (trialType | subids),
                  data = filter(df_expt3, trial_category == "test", block == "test",
                                     experiment == "replication", include_good_rt == "include"),
                  control = glmerControl(optimizer = "bobyqa"),
                  nAGQ = 1,
                  family = binomial)

knitr::kable(summary(m2_expt3)$coef, digits = 3)
```

#### Predict test performance from selecting target of gaze on exposure trials

```{r glmer total exposure correct}
m4_expt3 <- glmer(correct ~ total_exposure_correct * trialType + (trialType | subids),
                  control = glmerControl(optimizer = "bobyqa"),
                  data = filter(df_expt3, trial_category == "test", block == "test",
                                experiment == "replication", include_good_rt == "include"),
                  nAGQ = 1,
                  family = binomial)

knitr::kable(summary(m4_expt3)$coef, digits = 3)
```

Now we plot the new analysis: accuracy on test trials as a function of 
accuracy on exposure trials (selecting the gaze target).

#### Final plot 

```{r expt3 acc test expt 3 cogsci plot, echo=F}
expt3_acc_test <- ggplot(data=ms_test_test, 
                         aes(x=prop_cond_clean, y=accuracy, group=trialType,
                             color=trialType, label = trialType)) + 
    geom_pointrange(aes(ymin=accuracy - ci_low, 
                        ymax=accuracy + ci_high), size=1) +
    geom_smooth(method='lm', se=F) +
    geom_hline(aes(yintercept=1/4), linetype = "dashed") +
    scale_y_continuous(limits=c(0,1)) +
    # scale_colour_grey(start=0.3, end=0.6) +
    scale_colour_manual(values=c("#2c7fb8", "#e34a33")) +
    xlab("Reliability of Gaze") + 
    ylab("Proportion Correct") +
    labs(color = "Trial Type") +
    guides(color=FALSE) +
    theme(axis.title.x = element_text(colour="black",size=18,
                                      angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.title.y = element_text(colour="black",size=18,
                                      angle=90,hjust=0.5,vjust=0.8,face="plain"),
          axis.text.x = element_text(colour="grey20",size=12,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.text.y = element_text(colour="grey20",size=12,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          legend.text = element_text(size=13),
          legend.title = element_text(size=13, face="bold")) 
```

```{r expt3 chose gazetar analysis, echo = F}
expt3_acc_test_chose_gazetar <- ggplot(data=ms_acc_exp_test_expt3, 
                                       aes(x=total_exposure_correct, y=correct, group=trialType,
                                           color=trialType, label = trialType)) + 
    geom_pointrange(aes(ymin=correct - cil, 
                        ymax=correct + cih), size=1) +
    geom_smooth(method='lm', se=F) +
    geom_hline(aes(yintercept=1/4), linetype = "dashed") +
    scale_x_continuous(limits=c(0,8), breaks=c(0:8)) +
    scale_y_continuous(limits=c(0,1)) +
    #scale_colour_grey(start=0.3, end=0.6) +
    scale_colour_manual(values=c("#2c7fb8", "#e34a33")) +
    xlab("Num. Trials Used Gaze") + 
    ylab("") +
    labs(color = "Trial Type") +
    guides(color=FALSE) +
    theme(axis.title.x = element_text(colour="black",size=18,
                                      angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.title.y = element_text(colour="black",size=18,
                                      angle=90,hjust=0.5,vjust=0.8,face="plain"),
          axis.text.x = element_text(colour="grey20",size=12,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.text.y = element_text(colour="grey20",size=12,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          legend.text = element_text(size=13),
          legend.title = element_text(size=13, face="bold")) 
```

```{r expt3_subj_rel_plot paper, echo = F}
expt3_subj_rel_test_plot <- ggplot(data=ms_rel_subj, 
                                   aes(x=rel_bin, y=mean_accuracy, group=trialType,
                                       color=trialType, label = trialType)) + 
    geom_pointrange(aes(ymin=mean_accuracy - ci_low, 
                        ymax=mean_accuracy + ci_high), size=1) +
    geom_smooth(method='lm', se=F) +
    geom_hline(aes(yintercept=1/4), linetype = "dashed") +
    scale_y_continuous(limits=c(0,1)) +
    scale_colour_manual(values=c("#2c7fb8", "#e34a33")) +
    xlab("Subjective Reliability Judgment") + 
    ylab("") +
    labs(color = "Trial Type") +
    guides(color=FALSE) +
    theme(axis.title.x = element_text(colour="black",size=18,
                                      angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.title.y = element_text(colour="black",size=18,
                                      angle=90,hjust=0.5,vjust=0.8,face="plain"),
          axis.text.x = element_text(colour="grey20",size=12,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          axis.text.y = element_text(colour="grey20",size=12,
                                     angle=0,hjust=0.5,vjust=0,face="plain"),
          legend.text = element_text(size=13),
          legend.title = element_text(size=13, face="bold")) 
```

```{r expt3 final plot}
gridExtra::grid.arrange(expt3_acc_test, expt3_acc_test_chose_gazetar, expt3_subj_rel_test_plot, 
                        ncol = 3)
```