---
title: "Soc-Xsit Vizualizations and Models"
author: "Kyle MacDonald"
date: "January 17, 2015"
output: html_document
---

```{r global_options, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=10, fig.height=8, fig.crop = F, echo = F,
                      warning=FALSE, cache=F, message=FALSE, sanitize = T)
```

This script creates visualizations and models for our Social Cross-situational Word Learning Project.

Clear workspace and set working directory 

```{r clear workspace, echo=F, warning=F}
source("useful.R")
library(pander)
library(magrittr)
library(gridExtra)
library(tidyr)
library(langcog)
library(directlabels)
```

Read in data from all 3 Experiments:

* Experiment 1: Large scale experiment manipulating attention and memory demands
* Experiment 2: Replication of Experiment 1 with more ecologically valid stimulus set
* Experiment 3: Parametric manipulation of cue reliablity

```{r read data, echo=F, warning=F}
df_expt1 <- read.csv("../data/3_final-processed/soc-xsit-expt1-finalData.csv")
df_expt2 <- read.csv("../data/3_final-processed/soc-xsit-expt2-finalData.csv")
df_expt3 <- read.csv("../data/3_final-processed/soc-xsit-expt3-finalData.csv")
```

## Experiment 1

### Get the number of subjects in each condition.  

```{r describe data, tidy=TRUE}
nsubs <- df_expt1 %>%
  group_by(condition, intervalNum, numPicN) %>%
  summarise(n_subs = n_distinct(subids))

knitr::kable(nsubs)
```

### Set up filters 

Get test trials for analysis. Here we have 2 filters:

* Remove fast/slow RTs
* Remove fast/slow RTs & subjects who performed below 
chance selecting gaze target on exposure trials

```{r expt1 test trials}
# just RT filter
df_expo_expt1 <- df_expt1 %>%  
  filter(trial_category == "exposure", include_good_rt_exposure == "include")

df_test_expt1 <- df_expt1 %>%  
  filter(trial_category == "test", include_good_rt_test == "include",
         correct_exposure == T | condition == "No-Social")

# subject and trial level filter
df_test_expt1_filt <- df_expt1 %>% 
  filter(trial_category == "test") %>% 
  filter(include_good_rt_test == "include", 
         include_expo == "include" | condition == "No-Social") %>%
  filter(correct_exposure == T | condition == "No-Social")

df_expo_expt1_analysis <- df_expt1 %>%
  filter(trial_category == "exposure") %>% 
  filter(include_good_rt_exposure == "include", 
         include_expo == "include" | condition == "No-Social") %>%
  filter(correct_exposure == T | condition == "No-Social")
```

Get the number of subjects filtered out

```{r expt1 nsubs filtered}
df_n <- df_test_expt1 %>%
  group_by(condition) %>%
  summarise(n_subs = n_distinct(subids))

df_n_filt <- df_test_expt1_filt %>%
  group_by(condition) %>%
  summarise(n_subs_filt = n_distinct(subids)) %>%
  select(n_subs_filt)

df_n <- cbind(df_n, df_n_filt)

knitr::kable(df_n)
```

### Accuracy on exposure trials in social condition

Get means and CIs for each combination of number of referents and interval

```{r expt1 accuracy on exposure trials}
ms_expo_expt1 <-  df_expo_expt1 %>%
  filter(condition == "Social") %>%
  group_by(numPic, intervalNum, subids) %>%
  summarise(accuracy_exposure = mean(correct_exposure, na.rm = T)) %>% 
  group_by(numPic, intervalNum) %>%
  multi_boot_standard("accuracy_exposure")
```

Now plot those means and CIs.

```{r expt 1 accuracy on exposure trials plot, echo=F}
ggplot(data=ms_expo_expt1, aes(x=intervalNum, y=mean)) + 
  geom_pointrange(aes(ymin=ci_lower, 
                      ymax=ci_upper), size=0.6) +
  geom_smooth(method = "lm", se = F) +
  geom_hline(aes(yintercept=1/numPic), linetype = "dashed") +
  scale_x_continuous(limits=c(-.9,8), breaks=c(0, 1, 3, 7)) +
  scale_y_continuous(limits=c(0,1)) +
  scale_colour_manual(values=c("#1f78b4", "red")) +
  facet_grid( ~ numPic) + 
  xlab("Intervening Trials") + 
  ylab("Prop. Chose Gaze Target") +
  labs(colour = "Condition") +
  labs(linetype = "Trial Type") +
  guides(linetype=FALSE) +
  theme(text = element_text(size=14), 
        axis.title.y=element_text(vjust=1),
        axis.title.x=element_text(vjust=-0.3),
        legend.justification=c(0,0),
        legend.position = c(0,0)) 
```

### RT on exposure trials 

Next we compare reaction times across social/no-social at different 
levels of attention and memory demands.

```{r expt1 rt on exposure trials}
ms_expo_rt_expt1 <-  df_expo_expt1_analysis %>%
  mutate(rt = rt + 2000) %>% 
  group_by(numPic, intervalNum, condition, subids) %>%
  summarise(mean_rt = mean(rt)) %>% 
  group_by(numPic, intervalNum, condition) %>%
  multi_boot_standard("mean_rt")
```

Now we plot mean reaction times for each condition.

```{r expt1 rt labels, echo=F}
ms_expo_rt_expt1$condition <- revalue(ms_expo_rt_expt1$condition,
                                      c("No-Social" = "No-Gaze","Social" = "Gaze"))
```

```{r expt1 plot rt on exposure trials, echo=F}
ms_expo_rt_expt1$intervalNum <- as.factor(ms_expo_rt_expt1$intervalNum)
ms_expo_rt_expt1$numPic <- paste(ms_expo_rt_expt1$numPic, "-Referents", sep="")

exp1_rt_exposure_plot <- ggplot(data=ms_expo_rt_expt1, 
                                aes(x=intervalNum, y=mean, color = condition, 
                                    group = condition)) + 
  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper), size = 1) +
  geom_point(color = "white", size = 2.5, data = 
               filter(ms_expo_rt_expt1, condition == "No-Gaze")) +
  scale_y_continuous(limits=c(3000,7500)) +
  scale_colour_manual(values=c("#2c7fb8", "#e34a33")) +
  facet_grid( ~ numPic) + 
  xlab("Interval Between Exposure and Test") + 
  ylab("Reponse Time (ms)") +
  labs(colour = "Condition") +
  labs(linetype = "Trial Type") +
  guides(linetype=FALSE, color=F) +
  theme(title = element_text(size = 24),
        axis.title.x = element_text(colour="black",size=22,
                                    angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.text.x = element_text(colour="grey20",size=18,
                                   angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.text.y = element_text(colour="grey20",size=18,
                                   angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.title.y = element_text(colour="black",size=22,face="plain"),
        legend.position=c(0.1,0.2),
        legend.text = element_text(size=18),
        legend.title = element_text(size=20, face="bold"),
        strip.text = element_text(size=16),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_line(colour = "gray88", linetype = "solid"),
        panel.margin = unit(1, "lines"))
```

### Accuracy on test trials 

```{r expt1 acc test}
ms_test_expt1 <- df_test_expt1  %>%
  group_by(condition, intervalNum, numPic, trialType, subids) %>%
  summarise(accuracy = mean(correct), exclusionary_criteria = "Trial Level") %>% 
  group_by(condition, intervalNum, numPic, trialType) %>%
  multi_boot_standard("accuracy")

ms_test_filt_expt1 <- df_test_expt1_filt  %>%
  group_by(condition, intervalNum, numPic, trialType, subids) %>%
  summarise(accuracy = mean(correct), exclusionary_criteria = "Subject and Trial level") %>%
  group_by(condition, intervalNum, numPic, trialType) %>%
  multi_boot_standard("accuracy")

ms_test_all_expt1 <- rbind(ms_test_expt1, ms_test_filt_expt1)
```

```{r expt1 acc test plot revalue, echo=F}
ms_test_expt1$condition <- revalue(ms_test_expt1$condition,
                                   c("No-Social" = "No-Gaze","Social" = "Gaze"))
```

```{r expt1 acc test plot, echo=F}
ms_test_expt1 %<>%
  ungroup() %>% 
  mutate(intervalNum = as.factor(intervalNum),
         numPic_name = as.factor(paste(ms_test_expt1$numPic, "-Referents", sep="")))

expt1.acc.test <- ggplot(data=ms_test_expt1, aes(x=intervalNum, 
                                                 y=mean,colour = condition, 
                                                 lineType = trialType)) + 
  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper, shape = condition), 
                  fill = "white", stroke = 1.5, size= 1, fatten = 2.5,
                  position = position_jitter(width = .3)) +
  scale_shape_manual(values = c(21, 19)) +
  geom_hline(aes(yintercept=1/numPic), linetype = "dashed") +
  scale_y_continuous(limits=c(0,1.1), breaks = c(0, .25, .5, .75, 1.0)) +
  scale_colour_manual(values=c("#2c7fb8", "#e34a33")) +
  facet_grid(. ~ numPic_name) + 
  xlab("Interval Between Exposure and Test") + 
  ylab("Proportion Correct") +
  labs(colour = "Condition") +
  labs(linetype = "Trial Type") +
  guides(linetype=F, shape = F, color = F) +
  theme(axis.title.x = element_text(colour="black",size=22,
                                    angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.text.x = element_text(colour="grey20",size=18,
                                   angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.text.y = element_text(colour="grey20",size=18,
                                   angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.title.y = element_text(colour="black",size=22,face="plain"),
        legend.position=c(0.08,0.2),
        legend.text = element_text(size=18),
        legend.title = element_text(size=20, face="bold"),
        strip.text = element_text(size=16),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_line(colour = "gray88", linetype = "solid"),
        panel.margin = unit(1, "lines"))

grid.arrange(exp1_rt_exposure_plot, expt1.acc.test, ncol=1)
```

### LMERs

#### Predicting RT on exposure trials.

```{r expt1 lmer rt}
m1_rt_expt1 <- lmer(rt_exposure ~ condition * log2(intervalNum + 1) * log2(numPicN) + 
                      (1|subids), data=df_expo_expt1_analysis)

knitr::kable(summary(m1_rt_expt1)$coef, digits = 3)
```

## Experiment 2

In Experiment 2, we chose a subset of the referent/interval conditions: 
numPic = 4, and interval = 0 and 3.

Get the number of subjects in each condition.

```{r expt2 nsubs}
nsubs_expt2 <- df_expt2 %>% 
  group_by(condition, interval) %>%
  summarise(n_subs = n_distinct(subids))

knitr::kable(nsubs_expt2)
```

### Set up filters

Exposure trials.

```{r expt2 expo filters}
# just RT filter
df_expo_expt2 <- filter(df_expt2,
                        include_good_rt == "include",
                        condition_trial == "social",
                        trial_cat == "exposure")

# RT, subject level and trial level filter 
df_expo_expt2_filt <- filter(df_expt2,
                             trial_cat == "exposure",
                             condition_trial == "social" & mean_acc_exp > 0.25,
                             include_good_rt == "include")

# filter that gets both social/no-social trials
df_expo_expt2_analysis <- df_expt2 %>%
  mutate(rt = rt + 2000) %>% 
  filter(trial_cat == "exposure",
         mean_acc_exp > 0.25,
         correct_exposure = T | condition_trial == "no-social",
         include_good_rt == "include")
```

Get the number of subjects filtered out by the subject level filter.

```{r expt2 nsubs filtered}
df_n_expt2 <- df_expo_expt2 %>%
  group_by(condition) %>%
  summarise(n_subs = n_distinct(subids))

df_n_expt2_filt <- df_expo_expt2_filt %>%
  group_by(condition) %>%
  summarise(n_subs_filt = n_distinct(subids)) %>%
  select(n_subs_filt)

nsubs_expt2_filt <- cbind(df_n_expt2, df_n_expt2_filt)

knitr::kable(nsubs_expt2_filt)
```

Test trial filters.

```{r expt2 test filters}
# just RT filter
df_test_expt2 <- df_expt2 %>%
  filter(trial_cat == "test",
         include_good_rt == "include")

# RT, subject level and trial level filter 
df_test_expt2_filt <- df_expt2 %>%
  filter(trial_cat == "test",
         mean_acc_exp > 0.25 ,
         include_good_rt == "include",
         correct_exposure == T | condition_trial == "no-social")
```

### Analyze Exposure Trials

Accuracy, selecting target of gaze.

```{r expt2 acc expo}
# unfiltered
ms_expo_expt2 <- df_expo_expt2 %>%
  group_by(intervalNum, subids) %>%
  summarise(accuracy_exposure = mean(correct)) %>% 
  group_by(intervalNum) %>% 
  multi_boot_standard("accuracy_exposure") %>% 
  mutate(filter = "Unfiltered")

# filtered
ms_expo_expt2_filt <- df_expo_expt2_filt %>%
  group_by(intervalNum, subids) %>%
  summarise(accuracy_exposure = mean(correct)) %>% 
  group_by(intervalNum) %>% 
  multi_boot_standard("accuracy_exposure") %>% 
  mutate(filter = "Filtered")

ms_expo_all_expt2 <- rbind(ms_expo_expt2, ms_expo_expt2_filt)
```

```{r}
df_expo_expt2_analysis %>% 
  group_by(condition_trial) %>% 
  summarise(median_rt = median(rt),
            mean_rt = mean(rt))
```

RT on exposure trials.

```{r expt2 rt expo}
ms_rt_expo_expt2 <- df_expo_expt2_analysis %>%
  group_by(condition_trial, intervalNum, subids) %>%
  summarise(rt_exposure = mean(rt)) %>% 
  group_by(condition_trial, intervalNum) %>%
  multi_boot_standard("rt_exposure")
```

Plot RT differences

```{r expt2 rt expo plot, echo=F}
# revalue social/no-social --> gaze/no-gaze
ms_rt_expo_expt2$condition <- revalue(ms_rt_expo_expt2$condition,
                                      c("no-social" = "No-Gaze", "social" = "Gaze"))

expt2.rt.expo <- ggplot(data=ms_rt_expo_expt2, aes(x=as.factor(intervalNum), y=mean, 
                                                   color = condition, group = condition)) + 
  geom_line(size = 1) +
  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper, shape = condition), 
                  fill = "white", stroke = 2, size= 1.3, fatten = 3) +
  scale_shape_manual(values = c(21, 19)) +
  scale_y_continuous(limits=c(3000,6500)) +
  scale_colour_manual(values=c("#e34a33", "#2c7fb8")) +
  xlab("Interval Between Exposure and Test") +
  ylab("Response Time (ms)") +
  labs(colour = "Condition") +
  labs(linetype = "Trial Type") +
  guides(shape=F, color=F) +
  ggtitle("Study Time on Exposure Trials") + 
  theme(axis.title.x = element_text(colour="black",size=22,
                                    angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.text.x = element_text(colour="grey20",size=18,
                                   angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.text.y = element_text(colour="grey20",size=18,
                                   angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.title.y = element_text(colour="black",size=22,face="plain"),
        legend.text = element_text(size=20),
        legend.title = element_text(size=22, face="bold"),
        plot.title = element_text(lineheight=1, face="bold", size = 24),
        strip.text = element_text(size=16))
```

## Analyze test trials

Get means and CIs for each condition.

```{r expt2 acc test aggregate}
# unfiltered
ms_test_expt2 <- df_test_expt2 %>%
  group_by(trialType, condition_trial, intervalNum, subids) %>%
  summarise(accuracy = mean(correct)) %>% 
  group_by(trialType, condition_trial, intervalNum) %>% 
  multi_boot_standard("accuracy") %>% 
  mutate(filter = "Unfiltered")

# filtered (subject level)
ms_test_expt2_filt <- df_test_expt2_filt %>%
  group_by(trialType, condition_trial, intervalNum, subids) %>%
  summarise(accuracy = mean(correct)) %>% 
  group_by(trialType, condition_trial, intervalNum) %>% 
  multi_boot_standard("accuracy") %>% 
  mutate(filter = "Filtered")

ms_test_all_expt2 <- rbind(ms_test_expt2, ms_test_expt2_filt)
```

Now plot accuracy for test trials.

```{r expt2 acc test plot, echo=F}
# revalue social/no-social --> gaze/no-gaze
ms_test_expt2_filt$condition_trial <- revalue(ms_test_expt2_filt$condition_trial,
                                              c("no-social" = "No-Gaze", 
                                                "social" = "Gaze"))

## todo: fix geom_line to connect the correct points
expt2.acc.test <- ggplot(data=ms_test_expt2_filt, aes(x=as.factor(intervalNum), 
                                                      y=mean, colour = condition_trial)) + 
  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper, shape = condition_trial), 
                  fill = "white", stroke = 1.5, size= 1.3, fatten = 2.8,
                  position = position_jitter(width=.2)) +
  scale_shape_manual(values = c(21, 19)) +
  geom_hline(aes(yintercept=1/4), linetype = "dashed") +
  scale_y_continuous(limits=c(0,1)) +
  scale_colour_manual(values=c("#e34a33", "#2c7fb8")) +
  xlab("Interval Between Exposure and Test") +
  ylab("Proportion Correct") +
  labs(colour = "Condition") +
  labs(linetype = "Trial Type") +
  guides(linetype=FALSE, shape=F, color = F) +
  ggtitle("Accuracy on Test Trials") +
  theme(axis.title.x = element_text(colour="black",size=22,
                                    angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.text.x = element_text(colour="grey20",size=18,
                                   angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.text.y = element_text(colour="grey20",size=18,
                                   angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.title.y = element_text(colour="black",size=22,face="plain"),
        #legend.position=c(0.80,0.88),
        legend.text = element_text(size=20),
        legend.title = element_text(size=22, face="bold"),
        plot.title = element_text(lineheight=1, face="bold", size = 24),
        strip.text = element_text(size=16))

grid.arrange(expt2.rt.expo, expt2.acc.test, ncol=2)
```

## Experiment 3

```{r}
df_expt3 <- filter(df_expt3, experiment == "replication")
```

### Get the number of subjects in each experiment and condition.

```{r expt3 get number of subs}
n_subs_expt3 <- df_expt3 %>%
  group_by(prop_cond_clean, experiment) %>%
  summarise(n_subs = n_distinct(subids))

knitr::kable(n_subs_expt3)
```

Fix factor order for reliablity conditions

```{r, echo = F}
df_expt3$prop_cond_clean <- factor(df_expt3$prop_cond_clean,
                                   levels = c("0%", "25%", "50%", "75%", "100%"))
```

### Analyze performance on test block

Accuracy on familiarization trials in test block

```{r expt3 acc fam trials in test block}
ms_expo_test <- df_expt3 %>%
  filter(trial_category == "exposure", block == "test", 
         include_good_rt == "include", experiment == "replication") %>% 
  group_by(prop_cond_clean, subids) %>%
  summarise(accuracy = mean(correct_exposure, na.rm=T),
            mean_rel = mean(rel_subj, na.rm=T)) %>% 
  group_by(prop_cond_clean) %>% 
  multi_boot_standard("accuracy")
```

Now plot chose target of gaze

```{r chose gaze target plot}
ggplot(ms_expo_test, 
       aes(x=prop_cond_clean, y=mean, group=1)) +
  geom_smooth(method="lm", se=F, color="black") +
  geom_pointrange(aes(ymin=ci_lower,
                      ymax=ci_upper), size=1, color = "black") +
  geom_hline(yintercept=0.25, linetype = "dashed") +
  scale_y_continuous(limits=c(0,1)) +
  xlab("Level of Reliablity") + 
  ylab("Prop. Chose Target of Gaze") + 
  theme(axis.title.x = element_text(colour="black",size=16,
                                    angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.title.y = element_text(colour="black",size=16,
                                    angle=90,hjust=0.5,vjust=0.5,face="plain"),
        axis.text.x = element_text(colour="grey20",size=12,
                                   angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.text.y = element_text(colour="grey20",size=12,
                                   angle=0,hjust=0.5,vjust=0,face="plain"))

```

Accuracy on test trials in the test block

```{r expt3 acc on test trials test block}
ms_test_test <- df_expt3 %>%
  filter(trial_category == "test", block == "test", 
         include_good_rt == "include") %>% 
  group_by(prop_cond_clean, trialType, subids) %>%
  summarise(accuracy = mean(correct)) %>% 
  group_by(prop_cond_clean, trialType) %>% 
  multi_boot_standard("accuracy")
```

Analyze subject reported reliablity

```{r subjective reliablity analysis 1}
ms_test_subj_rel <- df_expt3 %>%
  filter(experiment == "replication") %>% 
  mutate(rel_subj = as.numeric(as.character(rel_subj))) %>% 
  group_by(prop_cond_clean, subids) %>%
  summarise(subjective_reliability = mean(rel_subj, na.rm=T)) %>% 
  group_by(prop_cond_clean) %>% 
  multi_boot_standard("subjective_reliability", na.rm = T)
```

Plot relationship between reliablity condition and subjective reliabiltiy judgments.

```{r}
qplot(x = prop_cond_clean, y = mean,
      group=1, data=ms_test_subj_rel) + 
  ylim(c(0,1)) +
  geom_smooth(method="lm", se=T) +
  xlab("Reliablity Condition") +
  ylab("Subjective Reliablity Judgment")
```

Summarise subjective reliablity at the participant level.

```{r expt3 summarise subjective reliablity}
mss_subj_rel <- df_expt3 %>% 
  filter(experiment == "replication", is.na(rel_subj) == F) %>% 
  select(subids, rel_subj, prop_cond_clean, total_exposure_correct, 
         same_accuracy, switch_accuracy, experiment) %>% 
  distinct()
```

Reported reliability vs. number correct on exposure - means.

```{r subjective reliablity analysis 3}
ms_test_subj_rel <- df_expt3 %>%
  filter(experiment == "replication", include_good_rt == "include", 
         is.na(rel_subj) == F) %>% 
  group_by(prop_cond_clean, total_exposure_correct, subids) %>%
  summarise(subj = mean(rel_subj, na.rm=TRUE)) %>% 
  group_by(prop_cond_clean, total_exposure_correct) %>% 
  multi_boot_standard("subj")
```

Plot.

```{r expt3 subj rel plot}
qplot(total_exposure_correct, mean, col = prop_cond_clean, 
      ymin = ci_lower, ymax = ci_upper,
      geom="pointrange",
      position=position_dodge(width=.1),
      data=ms_test_subj_rel, ylab="Subjective reliability", 
      xlab="Num Trials Chose Gaze Target") + 
  geom_smooth(method="lm", se=FALSE) +
  scale_color_discrete(name="Reliability Level") +
  theme(axis.title.x = element_text(colour="black",size=16,
                                    angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.title.y = element_text(colour="black",size=16,
                                    angle=90,hjust=0.5,vjust=0.5,face="plain"),
        axis.text.x = element_text(colour="grey20",size=12,
                                   angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.text.y = element_text(colour="grey20",size=12,
                                   angle=0,hjust=0.5,vjust=0,face="plain"),
        legend.text = element_text(size=13),
        legend.title = element_text(size=13, face="bold"))
```

Relationship between subjective reliability, reliablity condition, and test trial performance

```{r expt3 subj reliablity munging}
gather_mss_rel_subj <- mss_subj_rel %>% 
  gather(key = trialType, value = sub_mean_accuracy, 5:6) %>% 
  arrange(subids)

gather_mss_rel_subj$rel_bin <- cut(gather_mss_rel_subj$rel_subj, breaks = 5, 
                                   labels = c("0.0-0.2", "0.2-0.4", "0.4-0.6", 
                                              "0.6-0.8", "0.8-1.0" ))

ms_rel_subj <- gather_mss_rel_subj %>% 
  group_by(rel_bin, trialType, subids) %>% 
  summarise(mean_accuracy = mean(sub_mean_accuracy, na.rm = T)) %>% 
  group_by(rel_bin, trialType) %>% 
  multi_boot_standard("mean_accuracy", na.rm =T)
```

```{r expt3 acc test by acc exposure plot, echo=F}
ms_acc_exp_test_expt3 <- df_expt3 %>%
  filter(trial_category == "test", block == "test",
         include_good_rt == "include", experiment == "replication") %>% 
  group_by(trialType, total_exposure_correct, subids) %>%
  summarise(correct = mean(correct)) %>% 
  group_by(trialType, total_exposure_correct) %>% 
  multi_boot_standard("correct")
```

### Final plot 

```{r expt3 acc test expt 3 cogsci plot, echo=F}
expt3_acc_test <- ggplot(data=ms_test_test, 
                         aes(x=prop_cond_clean, y=mean, group=trialType,
                             color=trialType, label = trialType)) + 
  geom_smooth(method='lm', se=F) +
  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper, shape = trialType), 
                  fill = "white", stroke = 1.8, size= 1.3, fatten = 2.8) +
  scale_shape_manual(values = c(21, 19)) +
  geom_hline(aes(yintercept=1/4), linetype = "dashed") +
  scale_y_continuous(limits=c(0,1)) +
  scale_colour_manual(values=c("#2c7fb8", "#e34a33")) +
  xlab("Reliability of Gaze") + 
  ylab("Proportion Correct") +
  labs(color = "Trial Type") +
  guides(color=FALSE,shape=F) +
  theme(axis.title.x = element_text(colour="black",size=18,
                                    angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.title.y = element_text(colour="black",size=18,
                                    angle=90,hjust=0.5,vjust=0.8,face="plain"),
        axis.text.x = element_text(colour="grey20",size=12,
                                   angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.text.y = element_text(colour="grey20",size=12,
                                   angle=0,hjust=0.5,vjust=0,face="plain"),
        legend.text = element_text(size=13),
        legend.title = element_text(size=13, face="bold")) 
```

```{r expt3 chose gazetar analysis, echo = F}
expt3_acc_test_chose_gazetar <- ggplot(data=ms_acc_exp_test_expt3, 
                                       aes(x=total_exposure_correct, y=mean,
                                           group=trialType, color=trialType, 
                                           label = trialType)) + 
  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper, shape = trialType), 
                  fill = "white", stroke = 1.8, size= 1.3, fatten = 2.8) +
  scale_shape_manual(values = c(21, 19)) +
  geom_smooth(method='lm', se=F) +
  geom_hline(aes(yintercept=1/4), linetype = "dashed") +
  scale_x_continuous(limits=c(0,8), breaks=c(0:8)) +
  scale_y_continuous(limits=c(0,1)) +
  scale_colour_manual(values=c("#2c7fb8", "#e34a33")) +
  xlab("Num. Trials Used Gaze") + 
  ylab("") +
  labs(color = "Trial Type") +
  guides(color=FALSE,shape=F) +
  theme(axis.title.x = element_text(colour="black",size=18,
                                    angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.title.y = element_text(colour="black",size=18,
                                    angle=90,hjust=0.5,vjust=0.8,face="plain"),
        axis.text.x = element_text(colour="grey20",size=12,
                                   angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.text.y = element_text(colour="grey20",size=12,
                                   angle=0,hjust=0.5,vjust=0,face="plain"),
        legend.text = element_text(size=13),
        legend.title = element_text(size=13, face="bold")) 

expt3_subj_rel_test_plot <- ggplot(data=ms_rel_subj, 
                                   aes(x=rel_bin, y=mean, group=trialType,
                                       color=trialType, label = trialType)) + 
  geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper, shape = trialType), 
                  fill = "white", stroke = 1.8, size= 1.3, fatten = 2.8) +
  scale_shape_manual(values = c(21, 19)) +
  geom_smooth(method='lm', se=F) +
  geom_hline(aes(yintercept=1/4), linetype = "dashed") +
  scale_y_continuous(limits=c(0,1)) +
  scale_colour_manual(values=c("#2c7fb8", "#e34a33")) +
  xlab("Subjective Reliability Judgment") + 
  ylab("") +
  labs(color = "Trial Type") +
  guides(color=FALSE,shape=F) +
  theme(axis.title.x = element_text(colour="black",size=18,
                                    angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.title.y = element_text(colour="black",size=18,
                                    angle=90,hjust=0.5,vjust=0.8,face="plain"),
        axis.text.x = element_text(colour="grey20",size=12,
                                   angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.text.y = element_text(colour="grey20",size=12,
                                   angle=0,hjust=0.5,vjust=0,face="plain"),
        legend.text = element_text(size=13),
        legend.title = element_text(size=13, face="bold")) 

gridExtra::grid.arrange(expt3_acc_test, expt3_acc_test_chose_gazetar,
                        expt3_subj_rel_test_plot, ncol = 3)
```

### Inspection time analysis

Here we plot accuracy at test as a function of how long participants inspected the display during exposure at the trial level. 

First we need to get RT on exposure for each test trial

```{r}
df_inspect <- df_expt3 %>% 
  filter(trial_category == "exposure") %>% 
  select(subids, itemNum, inspection_time_exposure = rt) %>% 
  left_join(filter(df_expt3, trial_category == "test"), by = c("subids", "itemNum")) 
```
